\chapter[Experiment]{Experiment}
\label{cp:experiment}

{
% \parindent0pt


\section{Objectives}


The primary goal of the experiments is to rigorously evaluate the effectiveness of the proposed diversity-enhancing strategies and their multi-hybrid combinations within the Particle Swarm Optimization (PSO) framework. Specifically, the experiments aim to compare the performance of the proposed PSO variants against two benchmarks: the canonical PSO and a basic diversity-injected variant (PerturbationPSO). This comparison provides a clear reference for assessing how informed diversity mechanisms differ from uninformed, random perturbations.

An additional objective is to isolate and quantify the individual contribution of each learning strategy intended to enhance swarm diversity, as well as to examine the effects of systematically combining different particle roles within hybrid frameworks.
The experimental study may thus be viewed as organized around three main groups of algorithms:
\begin{itemize}
    \item Baselines:
  Two baseline algorithms are employed for benchmarking:
    \begin{itemize}
        \item PSO: The standard (or ``canonical'') PSO formulation without any explicit diversity-enhancing mechanism, serving as the foundational reference.
        
        \item PerturbationPSO: A simple extension of the canonical PSO that introduces Gaussian noise into particle positions after each update. This variant represents a naive, uninformed form of diversity injection occasionally found in the literature and highlights the contrast with structured, role-informed strategies.
    \end{itemize}
    
    \item Single diversity-enhancing strategies:
    These include individual role-based extensions that introduce informed exploration by means of
    \begin{itemize}
        \item repulsion from the best solutions (opposing-best strategies): RebelPSO, RejectorPSO, and RebelRejectorPSO;
        \item attraction to the worst solutions (negative learning strategies): ContrarianPSO, DefeatistPSO, and ContrarianDefeatistPSO;
        \item repulsion from the worst solutions (reverse learning strategies): EschewerPSO, EscapistPSO, and EschewerEscapistPSO.
    \end{itemize}
    % (i)   (ii)  or (iii) 
    
    \item Multi-hybrid strategies:    
      These include more advanced frameworks that combine multiple roles within or across the cognitive and social components of the velocity update equation: HybridFullDisjointPSO, HybridPartialDisjointPSO and HybridAdditivePSO.
\end{itemize}

% * **Single Diversity-Enhancing Strategies:**
%   These include individual role-based extensions that introduce informed exploration by means of (i) repulsion from the best solutions (opposing-best strategies),  (ii) attraction to the worst solutions (negative learning strategies), or (iii) repulsion from the worst solutions (reverse learning strategies).

% * **Multi-Hybrid Strategies:**
%   These are more advanced frameworks that combine multiple roles within or across the cognitive and social components of the velocity update equation, aiming to achieve a balance between exploration and exploitation.

% * **Baselines:**
%   Two baseline algorithms are employed for robust benchmarking:

%   * *Canonical PSO:* The standard PSO formulation without any explicit diversity-enhancing mechanism, serving as the foundational reference.
%   * *PerturbationPSO:* A simple extension of the canonical PSO that introduces Gaussian noise into particle positions after each update. This variant represents a naive, uninformed form of diversity injection occasionally found in the literature and highlights the contrast with structured, role-informed strategies.








\section{Benchmark Problems}\label{sec:benchmark-problems}

The selection of benchmark problems is critical, as algorithm performance can be significantly influenced by the characteristics of the chosen test suite. To ensure a comprehensive and fair evaluation, the algorithms are tested on a set of well-established continuous benchmark functions commonly used in the swarm intelligence and evolutionary computation literature. The suite employed in this study was designed to encompass a variety of problem features that challenge different aspects of the proposed optimization algorithms. The CEC (Congress on Evolutionary Computation) special sessions, for instance, have been instrumental in defining widely adopted benchmark sets and evaluation protocols. Here, I combine CEC functions \citep{liang2013cec2013,wu2017cec2017} with classic test functions \citep{jamil2013survey}, motivated by studies showing that algorithms tailored to perform well on specific CEC suites may exhibit significantly degraded performance on older, higher-dimensional, or real-world problems---especially when the computational budget is constrained \citep{piotrowski2023benchmark}.



% The algorithms were tested on the following 37 functions: Alpine N.1, Crowned Cross, Egg Holder, Expanded Shaffer, Generalized Schaffer N‑1 to N‑4, Generalized Schmidt–Vetters, Lennard‑Jones Minimum Energy Cluster, Michalewicz, Mishra‑03 to Mishra‑05, Modified Rosenbrock 02, Salomon, Schwefel N.2.0, N.2.6, N.3.6, N.6, Shubert N.3 and N.4, Sine Envelope, Stochastic, Stretched V, Styblinski–Tang, Rotated High Conditioned Elliptic, Rotated Bent Cigar, Rotated Discus, Shifted and Rotated Rosenbrock’s, Shifted Schwefel’s, Shifted and Rotated Schwefel’s, Shifted and Rotated HappyCat, Shifted and Rotated HGBat, Shifted and Rotated Weierstrass, Shifted and Rotated Expanded Griewank’s plus Rosenbrock’s, and Shifted and Rotated Expanded Scaffer’s F6.


The algorithms were tested on the 32 functions listed in Table~\ref{tab:benchmark-functions}. Each function is scalable and was tested in multiple dimensions, \(d \in \{100, 500, 1000\}\), with search bounds (and known optima) defined according to standard references.
% This setup provides a robust testbed to assess the algorithms under varying levels of complexity and scalability.


\begin{longtable}[c]{p{0.8cm}p{6.4cm}ll}
\caption{Benchmark functions used in this study.}
\label{tab:benchmark-functions} \\
\toprule
\textbf{Eq.} & \textbf{Function Name} &  \textbf{Known Optimum} & \textbf{Search Domain} \\ \midrule
\endfirsthead

\multicolumn{4}{c}%
{{\textit{\bfseries Table \thetable\ continued from previous page.}}} \\
\toprule
\textbf{Eq.} & \textbf{Function Name} & \textbf{Known Optimum} & \textbf{Search Domain} \\ \midrule
\endhead

\bottomrule
\addlinespace[1mm]
\multicolumn{4}{r}%
{{\textit{Continued on the next page.}}} \\
\endfoot

\bottomrule
\endlastfoot

\eqref{ben:alpine} & Alpine N.1  & $f_{\min}=0$ & $[-10,10]^d$ \\
\eqref{ben:crowned_cross} & Crowned Cross   & $f_{\min}=0.0001$ & $[-10,10]^d$ \\
\eqref{ben:eggHolder} & Egg Holder   & depends on $d$ & $[-512,512]^d$ \\
\eqref{ben:expandedShaffer} & Expanded Shaffer (F6)  & $f_{\min}=0$ & $[-100,100]^d$ \\
\eqref{ben:generalizedSchafferN1} & Generalized Schaffer N‑1  & $f_{\min}=0$ & $[-50,50]^d$ \\
\eqref{ben:generalizedSchafferN2}  & Generalized Schaffer N‑2   & $f_{\min}=0$ & $[-50,50]^d$ \\
\eqref{ben:generalizedSchafferN3}  & Generalized Schaffer N‑3  & $f_{\min}=0$ & $[-50,50]^d$ \\
\eqref{ben:generalizedSchafferN4}  & Generalized Schaffer N‑4 & $f_{\min}=0$ & $[-50,50]^d$ \\
\eqref{ben:generalizedSchmidtVetters} & Generalized Schmidt–Vetters & $f_{\min}=0$ & $[-100,100]^d$ \\
\eqref{ben:lennardJonesMinimumEnergyCluster} & Lennard‑Jones Minimum Energy Cluster & depends on $d$ & $[-80,80]^d$ \\
\eqref{ben:michalewicz} & Michalewicz & depends on $d$ & $[0,\pi]^d$ \\
\eqref{ben:Mishra03} & Mishra‑03 & depends on $d$ & $[-10,10]^d$ \\
\eqref{ben:Mishra04}  & Mishra‑04 & depends on $d$ & $[-10,10]^d$ \\
% \eqref{ben:Mishra05}  & Mishra‑05 & $f_{\min}\approx -0.119829$ & $[-10,10]^d$ \\
\eqref{ben:RosenbrockModified02} & Modified Rosenbrock N.2 & $f_{\min}=0$ & $[-30,30]^d$ \\
\eqref{ben:RotatedBentCigar} & Rotated Bent Cigar & $f_{\min}=0$ & $[-100,100]^d$ \\
\eqref{ben:RotatedDiscus} & Rotated Discus & $f_{\min}=0$ & $[-100,100]^d$ \\
\eqref{ben:RotatedHighConditionedElliptic} & Rotated High Conditioned Elliptic & $f_{\min}=0$ & $[-100,100]^d$ \\
\eqref{ben:Salomon} & Salomon & $f_{\min}=0$ & $[-100,100]^d$ \\
\eqref{ben:SchwefelN20} & Schwefel N.2.0 & $f_{\min}=0$ & $[-100,100]^d$ \\
% \eqref{ben:SchwefelN26} & Schwefel N.2.6 & $f_{\min}=0$ & $[-500,500]^d$ \\
\eqref{ben:SchwefelN36} & Schwefel N.3.6 & $f_{\min} = (d\!-\!1)\,4.8\times10^8$ & $[-500,500]^d$ \\
\eqref{ben:SchwefelN6} & Schwefel N.6 & $f_{\min}=0$ & $[-100,100]^d$ \\
\eqref{ben:ShiftedSchwefel} & Shifted Schwefel (N.2.6)  & $f_{\min}=0$ & $[-500,500]^d$ \\
% \eqref{ben:ShiftedRotatedExpGriewankRosenbrock} & Shifted and Rotated Expanded Griewank plus Rosenbrock & $f_{\min}=-130$ & $[-100,100]^d$ \\
\eqref{ben:ShiftedRotatedHappyCat} & Shifted and Rotated HappyCat & $f_{\min} = 0$ & $[-5,5]^d$ \\
\eqref{ben:ShiftedRotatedHGBat} & Shifted and Rotated HGBat & $f_{\min} = 0$ & $[-5,5]^d$ \\
% 29 & Shifted and Rotated Rosenbrock & -- & -- \\
\eqref{ben:ShiftedRotatedSchafferF7} & Shifted and Rotated Schaffer F7 & $f_{\min}=0$ & $[-100,100]^d$ \\
% 30 & Shifted and Rotated Schwefel & -- & -- \\
\eqref{ben:ShiftedRotatedWeierstrass} & Shifted and Rotated Weierstrass & $f_{\min} = 4d\,(1\!-\!0.5^{21})$ & $[-0.5,\,0.5]^d$ \\
\eqref{ben:ShubertN3} & Shubert N.3 & depends on $d$ & $[-10,10]^d$ \\
\eqref{ben:ShubertN4} & Shubert N.4 & depends on $d$ & $[-10,10]^d$ \\
\eqref{ben:SineEnvelope} & Sine Envelope & $f_{\min} = 0$ & $[-100,100]^d$ \\
\eqref{ben:Stochastic} & Stochastic & $f_{\min} = 0$ & $[-5,5]^d$ \\
\eqref{ben:StretchedV} & Stretched V & $f_{\min} = 0$ & $[-10,10]^d$ \\
\eqref{ben:StyblinskiTang} & Styblinski–Tang & $f_{\min} = -39.16617d$ & $[-5,5]^d$ \\
\end{longtable}

The selected functions cover a wide range of characteristics: they are single-objective, continuous (real-parameter), unconstrained but defined over bounded domains, scalable, high-dimensional, unimodal or multimodal, and include both differentiable and non-differentiable benchmark problems. This diversity ensures that the algorithms are evaluated across both smooth convex basins and rugged, multi-peaked topologies. Mathematical formulations of the benchmark functions \eqref{ben:alpine}-\eqref{ben:StyblinskiTang}, together with visualizations of their landscapes (Figure~\ref{fig:benchmark_problems_plot}), are provided in \autoref{app:benchmarks_formulas}.



% The selected functions cover a wide range of characteristics: single-objective, continuous (real-parameter), constrained, scalable, high-dimensional, unimodal and multimodal, differentiable and non-differentiable landscapes. Their
% % characteristics together with
% mathematical formulation is provided in \autoref{app:benchmarks_formulas}. This diversity is meant to ensure that the algorithms are evaluated across smooth convex basins as well as rugged and multi-peaked topologies.








\section{Experimental Setup}

% \subsection{Parameter Tuning}

The effectiveness of the proposed novel \glspl{metaheuristic} depends critically on the synergistic tuning of their dedicated parameters alongside the traditional PSO settings. In this study, the parameters for each PSO variant---including the baseline algorithms---were tuned using a systematic and rigorous procedure to ensure a fair and meaningful comparison.

Parameter tuning was conducted using the \texttt{irace} (Iterated Racing for Automatic Algorithm Configuration) methodology and its associated R package \citep{lopezibanez2016irace}. This approach involves an iterative process: new candidate configurations are sampled from a distribution, a racing procedure selects the best-performing configurations, and the sampling distribution is then updated to bias future sampling toward superior configurations. This process continues until a predefined tuning budget specified by the maximum number of algorithm evaluations or total computation time is exhausted.

For each algorithm, \texttt{irace} was configured with a budget of 1000 candidate configurations per parameter. Tuning was performed on three representative optimization problems---Sphere, Rastrigin, and Ackley---chosen to cover diverse landscape characteristics \citep{los2018misfit}. These instances were defined with 100 variables (i.e., a solution dimensionality of 100) and a maximum of 25000 objective function evaluations per run. The swarm size was fixed systematically at 100 particles throughout. To account for the stochastic nature of the algorithms, each candidate configuration was evaluated through five independent runs per problem instance. Importantly, these specific problem instances were used exclusively for tuning and were excluded from the benchmark suite used for the final experimental evaluation.

The implementation of all PSO variants and the experimentation were carried out using the \texttt{jMetalPy} Python framework \citep{benitezhidalgo2019jmetalpy}. All algorithms, including the baselines, were implemented from scratch in compliance with the framework’s interface specifications. The \texttt{jMetalPy} environment was chosen for its modular architecture, support for parallel execution, and seamless integration with Python’s scientific computing ecosystem, which ensured reproducibility and streamlined experimentation.

Both the parameter tuning and the final experimentation were executed on the Ares supercomputer at Cyfronet. Computations ran on the main partition, comprising more than 532 nodes with 48 cores each, equipped with dual Intel(R) Xeon(R) Platinum 8268 CPUs at 2.90\,GHz. To match the requirements of each phase efficiently, the requested computational resources were scaled accordingly, as detailed below:

\vspace{.835em}
\begin{tcbraster}[
    raster columns=2, 
    raster equal height, 
    nobeforeafter, 
    raster column skip=2cm
]
\begin{blkblock}{Parameter Tuning (irace):}
    \begin{verbatim}#SBATCH --nodes=1
#SBATCH --ntasks=48
#SBATCH --cpus-per-task=1
#SBATCH --mem=8G\end{verbatim}
\end{blkblock}
\begin{blkblock}{Empirical Experimentation:}
    \begin{verbatim}#SBATCH --nodes=1
#SBATCH --ntasks=1
#SBATCH --cpus-per-task=25
#SBATCH --mem=8G\end{verbatim}
\end{blkblock}
\end{tcbraster}
\vspace{.835em}

\noindent This difference in requested resources reflects that \texttt{irace} is an R-based tool with a distinct parallelization model compared to the Python-based experimentation framework.

The final set of tuned parameters is presented in Table~\ref{tab:parameter_configuration}, and parallel coordinates plots illustrating the distribution of sampled parameter configurations are provided in Figure~\ref{fig:parameter_plots}. Both the table and the plots are included in \autoref{app:optimization results} for reference.

Once the tuning phase was completed and the optimal parameter configurations were identified for each algorithm, the main experimentation phase was carried out to systematically evaluate and compare all variants under diverse benchmark conditions. During this phase, each algorithm was executed on the full suite of benchmark problems described in \autoref{sec:benchmark-problems}, using the tuned parameters and a consistent termination condition.

Each algorithm was run for 50 independent executions to rigorously assess its effectiveness and to capture variability due to stochastic behaviour. For each run, the final fitness value of the best solution found was recorded. The primary measure of solution quality is therefore the mean final fitness across all runs for each benchmark problem and dimensionality. These results, along with the associated standard deviations, are presented in Table~\ref{tab:final_results}.

In addition to evaluating final solution quality, convergence speed was analyzed by generating convergence curves that depict the mean fitness over iterations for each algorithm, averaged across the 50 independent runs. These curves, presented in Figures~\ref{fig:results100}–\ref{fig:results1000} within \autoref{app:detailed_results}, provide insight into how quickly and reliably each variant approaches high-quality solutions. Robustness was quantified by calculating the standard deviation of final fitness values, with lower standard deviation indicating greater consistency across runs. The spread and variability of the final fitness values are further illustrated by the raincloud distribution plots included alongside the convergence curves in the same figures.

% In addition to final solution quality, convergence speed was analyzed by generating convergence curves that show the mean fitness over iterations for each algorithm, averaged across the 50 runs. These curves, shown in Figures~\ref{fig:results100}-\ref{fig:results1000} in the \autoref{app:detailed_results}, provide insight into how quickly and reliably each variant approaches high-quality solutions. Robustness was quantified by calculating the standard deviation of final fitness values, with a lower standard deviation indicating greater consistency across runs. The spread of final fitness values is further visualized through distribution plots in the same figures.

To ensure fair comparison, the termination criterion for all runs was consistently set to a maximum of 25000 objective function evaluations. Given the fixed swarm size of 100 particles, this configuration implies exactly 250 algorithm iterations per run for every tested variant. This systematic setup guarantees that all algorithms operated under the same computational budget and search effort, supporting a meaningful and unbiased performance assessment.







%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The effectiveness of the proposed novel \glspl{metaheuristic} hinges on the synergistic tuning of their dedicated parameters alongside the traditional PSO settings. In this study, the parameters for each PSO variant---including the baseline algorithms---were tuned using the same systematic and rigorous procedure to ensure a fair and meaningful comparison.

% Parameter tuning was conducted using the \texttt{irace} (Iterated Racing for Automatic Algorithm Configuration) methodology and its associated R package \citep{lopezibanez2016irace}. The core mechanism involves an iterative process: new algorithm configurations are sampled from a distribution; a racing procedure is then used to select the best-performing configurations; finally, the sampling distribution is updated to bias future samples toward the superior configurations. This refinement continues until a predefined tuning budget---such as a maximum number of algorithm executions or total computation time---is reached.

% For each algorithm, \texttt{irace} was configured with a total budget of 1000 candidate configurations per algorithm parameter. Tuning was performed using three representative optimization problems: Sphere, Rastrigin, and Ackley. These functions were chosen to cover diverse landscape features. It is important to note that these specific problem instances were used exclusively during the tuning phase and were then removed from the benchmark problem set used for the final empirical evaluation. Problems were defined with 100 variables (i.e., a solution dimensionality of 100), and a maximum of 25000 objective function evaluations per run. The swarm size for each algorithm was systematically fixed at 100. To account for the stochastic nature of the algorithms, each candidate configuration was evaluated through five independent runs per problem instance. 

% The algorithm implementation and experimentation were carried out using the \texttt{jMetalPy} Python framework \citep{benitezhidalgo2019jmetalpy}. All algorithms, including the baselines, were implemented from scratch, adhering to the package’s interface specifications.

% Both parameter tuning and experimental runs were executed on the Ares supercomputer at Cyfronet. Computations were performed on its main partition, which comprises over 532 nodes, each with 48 cores and dual Intel(R) Xeon(R) Platinum 8268 CPUs running at 2.90\,GHz. Naturally, the requested computational resources were scaled to match the practical requirements of each phase, as detailed below:

% \vspace{.835em}
% \begin{tcbraster}[
%     raster columns=2, 
%     raster equal height, 
%     nobeforeafter, 
%     raster column skip=2cm
% ]
% \begin{blkblock}{Parameter Tuning (irace):}
%     \begin{verbatim}#SBATCH --nodes=1
% #SBATCH --ntasks=48
% #SBATCH --cpus-per-task=1
% #SBATCH --mem=8G\end{verbatim}
% \end{blkblock}
% \begin{blkblock}{Empirical Experimentation:}
%     \begin{verbatim}#SBATCH --nodes=1
% #SBATCH --ntasks=1
% #SBATCH --cpus-per-task=25
% #SBATCH --mem=8G\end{verbatim}
% \end{blkblock}
% \end{tcbraster}
% \vspace{.835em}
% The difference in requested resources reflects that the \texttt{irace} package is an R-based tool with a distinct parallelization model compared to the Python-based experimentation framework.

% The final set of tuned parameters is presented in the Table~\ref{tab:parameter_configuration}. Parallel coordinates plots showing the distribution of parameter configurations is presented on Figure~\ref{fig:parameter_plots}. Both Table and plots are inserted in \autoref{app:optimization results}.


% Once the tuning phase was completed and the best-performing parameter configurations were identified for each algorithm, the main experimentation phase was conducted to systematically evaluate and compare the algorithms under diverse benchmark conditions. During this phase, each algorithm variant was executed on the full suite of benchmark problems described in \autoref{sec:benchmark-problems}, using the tuned parameters and a consistent termination criterion. The following paragraphs detail the performance metrics used to analyse solution quality, convergence behaviour, and robustness across all tested configurations.

% Each algorithm was executed for 50 independent runs to rigorously evaluate its effectiveness and to capture the variability inherent in stochastic metaheuristic search processes. For each run, the best solution found---i.e., the final fitness value---was recorded. The primary measure of solution quality is therefore the average final fitness across all runs for a given benchmark problem and dimensionality. These results, together with the associated standard deviations, are presented in Table~\ref{tab:final_results}.

% In addition to final solution quality, convergence speed is an important aspect of performance. To analyze this, convergence curves were generated for each algorithm, illustrating the mean fitness over iterations across the 50 runs. These plots, provided in Figure~\ref{fig:convergence_curves}, allow a visual assessment of how rapidly and steadily each variant approaches high-quality solutions over time.

% To assess the robustness of each algorithm, the standard deviation of the final fitness values was calculated for each test case. A lower standard deviation indicates that an algorithm consistently finds solutions of similar quality across repeated runs, which is particularly important when applied to real-world problems where repeatability is desired. The spread and distribution of final fitness values are further illustrated using final fitness distribution plots shown in Figure~\ref{fig:fitness_distributions}.

% To ensure consistency across all experiments, the termination criterion was systematically defined by a 25000 objective function evaluations. Given that the swarm size was fixed at 100 particles for all runs, this setup resulted in exactly 250 algorithm steps per run for every variant tested. This consistent configuration guarantees that performance comparisons remain fair and unbiased with respect to computational budget.



\section{Results and Analysis}

% The final average performance of each algorithm, assessed on each benchmark problem and for each tested dimensionality, is presented in Table~\ref{tab:final_results}.
% The table reports the mean final fitness values together with their standard deviations. For each problem and dimensionality, the best-performing algorithm is highlighted with boldface and grey cell background.

% This section presents a detailed analysis of the empirical results obtained for the proposed diversity-enhancing PSO variants and their multi-hybrid extensions. The primary aim is to evaluate their performance relative to the canonical PSO and the perturbation-based baseline across a diverse set of benchmark problems and dimensionalities. The results are analysed in terms of solution quality, convergence speed, and robustness, in line with the performance metrics defined in the previous section.  

% The analysis begins with a comparative overview of the average final fitness values and associated variability, providing quantitative evidence of the effectiveness of each variant. This is followed by an examination of the convergence behaviour, highlighting how different diversity mechanisms influence the balance between exploration and exploitation over time. Finally, the robustness of each algorithm is assessed through the distribution of final outcomes, illustrating the consistency of performance across independent runs.

% Together, these results offer insight into the practical benefits and limitations of incorporating informed, role-based diversity strategies within the PSO framework. Where appropriate, observations are supported by visual plots and statistical summaries to ensure clarity and facilitate objective comparison.





\begin{longtable}{c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c}
\caption[Average final fitness values]{Average final fitness values and standard deviations for all tested algorithms across benchmark problems and dimensions.}\label{tab:final_results}\\
\toprule
\adjustbox{angle=90}{\textbf{Problem}} & \textbf{$d$} & \adjustbox{angle=90}{\textbf{PSO}} & \adjustbox{angle=90}{\textbf{PerturbationPSO}} & \adjustbox{angle=90}{\textbf{RebelPSO}} & \adjustbox{angle=90}{\textbf{RejectorPSO}} & \adjustbox{angle=90}{\textbf{RebelRejectorPSO}} & \adjustbox{angle=90}{\textbf{ContrarianPSO}} & \adjustbox{angle=90}{\textbf{DefeatistPSO}} & \adjustbox{angle=90}{\textbf{ContrarianDefeatistPSO}} & \adjustbox{angle=90}{\textbf{EschewerPSO}} & \adjustbox{angle=90}{\textbf{EscapistPSO}} & \adjustbox{angle=90}{\textbf{EschewerEscapistPSO}} & \adjustbox{angle=90}{\textbf{HybridFullDisjointPSO}} & \adjustbox{angle=90}{\textbf{HybridPartialDisjointPSO}} & \adjustbox{angle=90}{\textbf{HybridAdditivePSO}} \\
\midrule
\endfirsthead

\multicolumn{16}{c}{\textit{\bfseries Table \thetable\ continued from previous page.}} \\
\toprule
\adjustbox{angle=90}{\textbf{Problem}} & \textbf{$d$} & \adjustbox{angle=90}{\textbf{PSO}} & \adjustbox{angle=90}{\textbf{PerturbationPSO}} & \adjustbox{angle=90}{\textbf{RebelPSO}} & \adjustbox{angle=90}{\textbf{RejectorPSO}} & \adjustbox{angle=90}{\textbf{RebelRejectorPSO}} & \adjustbox{angle=90}{\textbf{ContrarianPSO}} & \adjustbox{angle=90}{\textbf{DefeatistPSO}} & \adjustbox{angle=90}{\textbf{ContrarianDefeatistPSO}} & \adjustbox{angle=90}{\textbf{EschewerPSO}} & \adjustbox{angle=90}{\textbf{EscapistPSO}} & \adjustbox{angle=90}{\textbf{EschewerEscapistPSO}} & \adjustbox{angle=90}{\textbf{HybridFullDisjointPSO}} & \adjustbox{angle=90}{\textbf{HybridPartialDisjointPSO}} & \adjustbox{angle=90}{\textbf{HybridAdditivePSO}} \\
\midrule
\endhead

% \bottomrule
\addlinespace[1mm]
\multicolumn{16}{r}{\textit{Continued on the next page.}} \\
\endfoot

\bottomrule
\endlastfoot

\multirow{3}{*}{\centering\shortstack{\eqref{ben:alpine}}} & \makecell{\centering\shortstack{ 100}} & \adjustbox{angle=90}{\shortstack{3.10e-01\\{\scriptsize$\pm$2.17e-01}}} & \adjustbox{angle=90}{\shortstack{1.77e+01\\{\scriptsize$\pm$6.30e+00}}} & \adjustbox{angle=90}{\shortstack{7.18e-01\\{\scriptsize$\pm$1.38e+00}}} & \adjustbox{angle=90}{\shortstack{7.91e-01\\{\scriptsize$\pm$2.17e+00}}} & \adjustbox{angle=90}{\shortstack{3.20e-01\\{\scriptsize$\pm$3.29e-01}}} & \adjustbox{angle=90}{\shortstack{1.46e+00\\{\scriptsize$\pm$3.00e+00}}} & \adjustbox{angle=90}{\shortstack{8.39e-01\\{\scriptsize$\pm$1.87e+00}}} & \adjustbox{angle=90}{\shortstack{5.06e-01\\{\scriptsize$\pm$7.24e-01}}} & \adjustbox{angle=90}{\shortstack{4.56e-01\\{\scriptsize$\pm$9.22e-01}}} & \adjustbox{angle=90}{\shortstack{6.38e-01\\{\scriptsize$\pm$1.37e+00}}} & \adjustbox{angle=90}{\shortstack{5.89e-01\\{\scriptsize$\pm$1.41e+00}}} & \adjustbox{angle=90}{\shortstack{2.95e-01\\{\scriptsize$\pm$6.49e-01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{4.59e-02}\\{\scriptsize$\pm$\textbf{6.03e-02}}}} & \adjustbox{angle=90}{\shortstack{4.96e-01\\{\scriptsize$\pm$1.28e+00}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{1.75e+00\\{\scriptsize$\pm$1.72e+00}}} & \adjustbox{angle=90}{\shortstack{1.84e+02\\{\scriptsize$\pm$2.27e+01}}} & \adjustbox{angle=90}{\shortstack{2.50e+00\\{\scriptsize$\pm$3.84e+00}}} & \adjustbox{angle=90}{\shortstack{3.90e+00\\{\scriptsize$\pm$6.59e+00}}} & \adjustbox{angle=90}{\shortstack{1.68e+00\\{\scriptsize$\pm$1.60e+00}}} & \adjustbox{angle=90}{\shortstack{3.60e+00\\{\scriptsize$\pm$5.74e+00}}} & \adjustbox{angle=90}{\shortstack{3.43e+00\\{\scriptsize$\pm$6.53e+00}}} & \adjustbox{angle=90}{\shortstack{2.14e+00\\{\scriptsize$\pm$3.06e+00}}} & \adjustbox{angle=90}{\shortstack{1.40e+00\\{\scriptsize$\pm$1.10e+00}}} & \adjustbox{angle=90}{\shortstack{1.41e+00\\{\scriptsize$\pm$1.33e+00}}} & \adjustbox{angle=90}{\shortstack{2.93e+00\\{\scriptsize$\pm$4.18e+00}}} & \adjustbox{angle=90}{\shortstack{1.48e+00\\{\scriptsize$\pm$2.79e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.47e-01}\\{\scriptsize$\pm$\textbf{3.30e-01}}}} & \adjustbox{angle=90}{\shortstack{2.30e+00\\{\scriptsize$\pm$2.19e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{3.60e+00\\{\scriptsize$\pm$4.18e+00}}} & \adjustbox{angle=90}{\shortstack{4.40e+02\\{\scriptsize$\pm$5.18e+01}}} & \adjustbox{angle=90}{\shortstack{6.80e+00\\{\scriptsize$\pm$8.78e+00}}} & \adjustbox{angle=90}{\shortstack{8.76e+00\\{\scriptsize$\pm$1.68e+01}}} & \adjustbox{angle=90}{\shortstack{5.79e+00\\{\scriptsize$\pm$1.02e+01}}} & \adjustbox{angle=90}{\shortstack{7.68e+00\\{\scriptsize$\pm$8.58e+00}}} & \adjustbox{angle=90}{\shortstack{3.68e+00\\{\scriptsize$\pm$6.65e+00}}} & \adjustbox{angle=90}{\shortstack{2.48e+00\\{\scriptsize$\pm$1.80e+00}}} & \adjustbox{angle=90}{\shortstack{2.44e+00\\{\scriptsize$\pm$1.62e+00}}} & \adjustbox{angle=90}{\shortstack{2.96e+00\\{\scriptsize$\pm$2.75e+00}}} & \adjustbox{angle=90}{\shortstack{5.45e+00\\{\scriptsize$\pm$7.43e+00}}} & \adjustbox{angle=90}{\shortstack{3.93e+00\\{\scriptsize$\pm$6.60e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{5.39e-01}\\{\scriptsize$\pm$\textbf{4.81e-01}}}} & \adjustbox{angle=90}{\shortstack{4.98e+00\\{\scriptsize$\pm$5.37e+00}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:crowned_cross}}} & 100 & \adjustbox{angle=90}{\shortstack{2.09e-01\\{\scriptsize$\pm$9.93e-02}}} & \adjustbox{angle=90}{\shortstack{2.35e-01\\{\scriptsize$\pm$6.09e-02}}} & \adjustbox{angle=90}{\shortstack{2.09e-01\\{\scriptsize$\pm$8.83e-02}}} & \adjustbox{angle=90}{\shortstack{2.08e-01\\{\scriptsize$\pm$8.66e-02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{7.09e-02}\\{\scriptsize$\pm$\textbf{4.87e-02}}}} & \adjustbox{angle=90}{\shortstack{2.81e-01\\{\scriptsize$\pm$1.21e-01}}} & \adjustbox{angle=90}{\shortstack{2.17e-01\\{\scriptsize$\pm$1.05e-01}}} & \adjustbox{angle=90}{\shortstack{2.12e-01\\{\scriptsize$\pm$1.13e-01}}} & \adjustbox{angle=90}{\shortstack{1.77e-01\\{\scriptsize$\pm$8.59e-02}}} & \adjustbox{angle=90}{\shortstack{3.94e-01\\{\scriptsize$\pm$9.95e-02}}} & \adjustbox{angle=90}{\shortstack{2.41e-01\\{\scriptsize$\pm$9.96e-02}}} & \adjustbox{angle=90}{\shortstack{2.66e-01\\{\scriptsize$\pm$8.71e-02}}} & \adjustbox{angle=90}{\shortstack{3.55e-01\\{\scriptsize$\pm$8.60e-02}}} & \adjustbox{angle=90}{\shortstack{4.10e-01\\{\scriptsize$\pm$8.65e-02}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{1.94e-01\\{\scriptsize$\pm$1.06e-01}}} & \adjustbox{angle=90}{\shortstack{2.40e-01\\{\scriptsize$\pm$4.75e-02}}} & \adjustbox{angle=90}{\shortstack{2.38e-01\\{\scriptsize$\pm$1.15e-01}}} & \adjustbox{angle=90}{\shortstack{2.34e-01\\{\scriptsize$\pm$8.12e-02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{7.46e-02}\\{\scriptsize$\pm$\textbf{4.25e-02}}}} & \adjustbox{angle=90}{\shortstack{2.52e-01\\{\scriptsize$\pm$1.05e-01}}} & \adjustbox{angle=90}{\shortstack{1.70e-01\\{\scriptsize$\pm$7.18e-02}}} & \adjustbox{angle=90}{\shortstack{1.90e-01\\{\scriptsize$\pm$8.92e-02}}} & \adjustbox{angle=90}{\shortstack{2.03e-01\\{\scriptsize$\pm$8.79e-02}}} & \adjustbox{angle=90}{\shortstack{3.85e-01\\{\scriptsize$\pm$9.04e-02}}} & \adjustbox{angle=90}{\shortstack{2.04e-01\\{\scriptsize$\pm$1.02e-01}}} & \adjustbox{angle=90}{\shortstack{2.53e-01\\{\scriptsize$\pm$7.36e-02}}} & \adjustbox{angle=90}{\shortstack{3.58e-01\\{\scriptsize$\pm$7.66e-02}}} & \adjustbox{angle=90}{\shortstack{3.93e-01\\{\scriptsize$\pm$9.25e-02}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{1.77e-01\\{\scriptsize$\pm$8.67e-02}}} & \adjustbox{angle=90}{\shortstack{2.35e-01\\{\scriptsize$\pm$4.72e-02}}} & \adjustbox{angle=90}{\shortstack{2.41e-01\\{\scriptsize$\pm$1.01e-01}}} & \adjustbox{angle=90}{\shortstack{2.11e-01\\{\scriptsize$\pm$8.49e-02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{7.02e-02}\\{\scriptsize$\pm$\textbf{6.37e-02}}}} & \adjustbox{angle=90}{\shortstack{2.76e-01\\{\scriptsize$\pm$1.15e-01}}} & \adjustbox{angle=90}{\shortstack{1.77e-01\\{\scriptsize$\pm$7.42e-02}}} & \adjustbox{angle=90}{\shortstack{1.80e-01\\{\scriptsize$\pm$8.21e-02}}} & \adjustbox{angle=90}{\shortstack{1.86e-01\\{\scriptsize$\pm$7.75e-02}}} & \adjustbox{angle=90}{\shortstack{3.78e-01\\{\scriptsize$\pm$7.78e-02}}} & \adjustbox{angle=90}{\shortstack{2.22e-01\\{\scriptsize$\pm$1.09e-01}}} & \adjustbox{angle=90}{\shortstack{2.65e-01\\{\scriptsize$\pm$9.41e-02}}} & \adjustbox{angle=90}{\shortstack{3.70e-01\\{\scriptsize$\pm$8.11e-02}}} & \adjustbox{angle=90}{\shortstack{3.90e-01\\{\scriptsize$\pm$7.67e-02}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:eggHolder}}} & 100 & \adjustbox{angle=90}{\shortstack{-2.95e+04\\{\scriptsize$\pm$5.36e+03}}} & \adjustbox{angle=90}{\shortstack{-2.54e+04\\{\scriptsize$\pm$3.01e+03}}} & \adjustbox{angle=90}{\shortstack{-2.94e+04\\{\scriptsize$\pm$4.66e+03}}} & \adjustbox{angle=90}{\shortstack{-2.86e+04\\{\scriptsize$\pm$4.67e+03}}} & \adjustbox{angle=90}{\shortstack{-2.89e+04\\{\scriptsize$\pm$4.81e+03}}} & \adjustbox{angle=90}{\shortstack{-3.26e+04\\{\scriptsize$\pm$2.98e+03}}} & \adjustbox{angle=90}{\shortstack{-2.94e+04\\{\scriptsize$\pm$4.91e+03}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-3.44e+04}\\{\scriptsize$\pm$\textbf{4.77e+03}}}} & \adjustbox{angle=90}{\shortstack{-2.83e+04\\{\scriptsize$\pm$4.68e+03}}} & \adjustbox{angle=90}{\shortstack{-2.82e+04\\{\scriptsize$\pm$4.09e+03}}} & \adjustbox{angle=90}{\shortstack{-3.00e+04\\{\scriptsize$\pm$4.94e+03}}} & \adjustbox{angle=90}{\shortstack{-2.92e+04\\{\scriptsize$\pm$6.46e+03}}} & \adjustbox{angle=90}{\shortstack{-3.38e+04\\{\scriptsize$\pm$2.05e+03}}} & \adjustbox{angle=90}{\shortstack{-3.29e+04\\{\scriptsize$\pm$3.56e+03}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{-1.33e+05\\{\scriptsize$\pm$1.39e+04}}} & \adjustbox{angle=90}{\shortstack{-7.98e+04\\{\scriptsize$\pm$2.02e+04}}} & \adjustbox{angle=90}{\shortstack{-1.09e+05\\{\scriptsize$\pm$1.47e+04}}} & \adjustbox{angle=90}{\shortstack{-1.17e+05\\{\scriptsize$\pm$1.57e+04}}} & \adjustbox{angle=90}{\shortstack{-1.11e+05\\{\scriptsize$\pm$1.39e+04}}} & \adjustbox{angle=90}{\shortstack{-1.25e+05\\{\scriptsize$\pm$9.40e+03}}} & \adjustbox{angle=90}{\shortstack{-1.18e+05\\{\scriptsize$\pm$1.13e+04}}} & \adjustbox{angle=90}{\shortstack{-1.37e+05\\{\scriptsize$\pm$1.18e+04}}} & \adjustbox{angle=90}{\shortstack{-1.14e+05\\{\scriptsize$\pm$1.68e+04}}} & \adjustbox{angle=90}{\shortstack{-1.20e+05\\{\scriptsize$\pm$1.31e+04}}} & \adjustbox{angle=90}{\shortstack{-1.32e+05\\{\scriptsize$\pm$1.39e+04}}} & \adjustbox{angle=90}{\shortstack{-1.44e+05\\{\scriptsize$\pm$8.95e+03}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-1.51e+05}\\{\scriptsize$\pm$\textbf{4.09e+03}}}} & \adjustbox{angle=90}{\shortstack{-1.49e+05\\{\scriptsize$\pm$6.48e+03}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{-2.58e+05\\{\scriptsize$\pm$1.72e+04}}} & \adjustbox{angle=90}{\shortstack{-1.62e+05\\{\scriptsize$\pm$4.24e+04}}} & \adjustbox{angle=90}{\shortstack{-2.06e+05\\{\scriptsize$\pm$1.76e+04}}} & \adjustbox{angle=90}{\shortstack{-2.19e+05\\{\scriptsize$\pm$2.21e+04}}} & \adjustbox{angle=90}{\shortstack{-2.20e+05\\{\scriptsize$\pm$2.04e+04}}} & \adjustbox{angle=90}{\shortstack{-2.39e+05\\{\scriptsize$\pm$1.28e+04}}} & \adjustbox{angle=90}{\shortstack{-2.30e+05\\{\scriptsize$\pm$1.96e+04}}} & \adjustbox{angle=90}{\shortstack{-2.60e+05\\{\scriptsize$\pm$1.55e+04}}} & \adjustbox{angle=90}{\shortstack{-2.21e+05\\{\scriptsize$\pm$2.54e+04}}} & \adjustbox{angle=90}{\shortstack{-2.33e+05\\{\scriptsize$\pm$1.83e+04}}} & \adjustbox{angle=90}{\shortstack{-2.64e+05\\{\scriptsize$\pm$2.48e+04}}} & \adjustbox{angle=90}{\shortstack{-2.75e+05\\{\scriptsize$\pm$3.51e+04}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-2.94e+05}\\{\scriptsize$\pm$\textbf{3.66e+03}}}} & \adjustbox{angle=90}{\shortstack{-2.87e+05\\{\scriptsize$\pm$1.28e+04}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:expandedShaffer}}} & 100 & \adjustbox{angle=90}{\shortstack{4.05e+01\\{\scriptsize$\pm$5.37e+00}}} & \adjustbox{angle=90}{\shortstack{3.62e+01\\{\scriptsize$\pm$2.62e+00}}} & \adjustbox{angle=90}{\shortstack{2.88e+01\\{\scriptsize$\pm$9.56e+00}}} & \adjustbox{angle=90}{\shortstack{3.31e+01\\{\scriptsize$\pm$9.06e+00}}} & \adjustbox{angle=90}{\shortstack{3.65e+01\\{\scriptsize$\pm$8.89e+00}}} & \adjustbox{angle=90}{\shortstack{2.62e+01\\{\scriptsize$\pm$1.06e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.43e+01}\\{\scriptsize$\pm$\textbf{1.21e+01}}}} & \adjustbox{angle=90}{\shortstack{3.15e+01\\{\scriptsize$\pm$1.02e+01}}} & \adjustbox{angle=90}{\shortstack{3.72e+01\\{\scriptsize$\pm$7.45e+00}}} & \adjustbox{angle=90}{\shortstack{2.73e+01\\{\scriptsize$\pm$1.15e+01}}} & \adjustbox{angle=90}{\shortstack{3.50e+01\\{\scriptsize$\pm$8.62e+00}}} & \adjustbox{angle=90}{\shortstack{4.21e+01\\{\scriptsize$\pm$1.73e+00}}} & \adjustbox{angle=90}{\shortstack{4.10e+01\\{\scriptsize$\pm$1.45e+00}}} & \adjustbox{angle=90}{\shortstack{4.30e+01\\{\scriptsize$\pm$1.77e+00}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{1.96e+02\\{\scriptsize$\pm$4.03e+01}}} & \adjustbox{angle=90}{\shortstack{2.04e+02\\{\scriptsize$\pm$6.30e+00}}} & \adjustbox{angle=90}{\shortstack{1.28e+02\\{\scriptsize$\pm$5.46e+01}}} & \adjustbox{angle=90}{\shortstack{1.49e+02\\{\scriptsize$\pm$5.55e+01}}} & \adjustbox{angle=90}{\shortstack{1.61e+02\\{\scriptsize$\pm$5.59e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.18e+02}\\{\scriptsize$\pm$\textbf{5.01e+01}}}} & \adjustbox{angle=90}{\shortstack{1.34e+02\\{\scriptsize$\pm$5.22e+01}}} & \adjustbox{angle=90}{\shortstack{1.47e+02\\{\scriptsize$\pm$6.11e+01}}} & \adjustbox{angle=90}{\shortstack{1.91e+02\\{\scriptsize$\pm$4.19e+01}}} & \adjustbox{angle=90}{\shortstack{1.39e+02\\{\scriptsize$\pm$5.58e+01}}} & \adjustbox{angle=90}{\shortstack{1.46e+02\\{\scriptsize$\pm$5.22e+01}}} & \adjustbox{angle=90}{\shortstack{2.29e+02\\{\scriptsize$\pm$4.59e+00}}} & \adjustbox{angle=90}{\shortstack{2.29e+02\\{\scriptsize$\pm$3.57e+00}}} & \adjustbox{angle=90}{\shortstack{2.34e+02\\{\scriptsize$\pm$4.07e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{3.78e+02\\{\scriptsize$\pm$9.16e+01}}} & \adjustbox{angle=90}{\shortstack{4.32e+02\\{\scriptsize$\pm$1.02e+01}}} & \adjustbox{angle=90}{\shortstack{2.23e+02\\{\scriptsize$\pm$8.56e+01}}} & \adjustbox{angle=90}{\shortstack{2.94e+02\\{\scriptsize$\pm$9.66e+01}}} & \adjustbox{angle=90}{\shortstack{3.33e+02\\{\scriptsize$\pm$1.06e+02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.12e+02}\\{\scriptsize$\pm$\textbf{1.09e+02}}}} & \adjustbox{angle=90}{\shortstack{2.42e+02\\{\scriptsize$\pm$9.47e+01}}} & \adjustbox{angle=90}{\shortstack{2.74e+02\\{\scriptsize$\pm$1.14e+02}}} & \adjustbox{angle=90}{\shortstack{3.64e+02\\{\scriptsize$\pm$1.07e+02}}} & \adjustbox{angle=90}{\shortstack{2.21e+02\\{\scriptsize$\pm$1.18e+02}}} & \adjustbox{angle=90}{\shortstack{2.94e+02\\{\scriptsize$\pm$9.23e+01}}} & \adjustbox{angle=90}{\shortstack{4.70e+02\\{\scriptsize$\pm$5.22e+00}}} & \adjustbox{angle=90}{\shortstack{4.70e+02\\{\scriptsize$\pm$3.89e+00}}} & \adjustbox{angle=90}{\shortstack{4.79e+02\\{\scriptsize$\pm$6.55e+00}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:generalizedSchafferN1}}} & 100 & \adjustbox{angle=90}{\shortstack{2.67e+01\\{\scriptsize$\pm$1.33e+01}}} & \adjustbox{angle=90}{\shortstack{3.50e+01\\{\scriptsize$\pm$3.44e+00}}} & \adjustbox{angle=90}{\shortstack{1.77e+01\\{\scriptsize$\pm$1.38e+01}}} & \adjustbox{angle=90}{\shortstack{2.35e+01\\{\scriptsize$\pm$1.27e+01}}} & \adjustbox{angle=90}{\shortstack{2.59e+01\\{\scriptsize$\pm$1.28e+01}}} & \adjustbox{angle=90}{\shortstack{1.82e+01\\{\scriptsize$\pm$1.51e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.73e+01}\\{\scriptsize$\pm$\textbf{1.32e+01}}}} & \adjustbox{angle=90}{\shortstack{1.78e+01\\{\scriptsize$\pm$1.32e+01}}} & \adjustbox{angle=90}{\shortstack{2.55e+01\\{\scriptsize$\pm$1.23e+01}}} & \adjustbox{angle=90}{\shortstack{1.74e+01\\{\scriptsize$\pm$1.30e+01}}} & \adjustbox{angle=90}{\shortstack{2.21e+01\\{\scriptsize$\pm$1.46e+01}}} & \adjustbox{angle=90}{\shortstack{3.76e+01\\{\scriptsize$\pm$2.29e+00}}} & \adjustbox{angle=90}{\shortstack{3.77e+01\\{\scriptsize$\pm$1.66e+00}}} & \adjustbox{angle=90}{\shortstack{4.14e+01\\{\scriptsize$\pm$9.87e-01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{7.10e+01\\{\scriptsize$\pm$5.26e+01}}} & \adjustbox{angle=90}{\shortstack{2.19e+02\\{\scriptsize$\pm$6.15e+00}}} & \adjustbox{angle=90}{\shortstack{1.41e+02\\{\scriptsize$\pm$9.31e+01}}} & \adjustbox{angle=90}{\shortstack{1.59e+02\\{\scriptsize$\pm$9.28e+01}}} & \adjustbox{angle=90}{\shortstack{1.43e+02\\{\scriptsize$\pm$7.99e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{5.23e+01}\\{\scriptsize$\pm$\textbf{3.81e+01}}}} & \adjustbox{angle=90}{\shortstack{7.14e+01\\{\scriptsize$\pm$7.18e+01}}} & \adjustbox{angle=90}{\shortstack{7.15e+01\\{\scriptsize$\pm$5.98e+01}}} & \adjustbox{angle=90}{\shortstack{8.51e+01\\{\scriptsize$\pm$7.08e+01}}} & \adjustbox{angle=90}{\shortstack{1.51e+02\\{\scriptsize$\pm$9.76e+01}}} & \adjustbox{angle=90}{\shortstack{1.52e+02\\{\scriptsize$\pm$8.85e+01}}} & \adjustbox{angle=90}{\shortstack{2.19e+02\\{\scriptsize$\pm$1.44e+01}}} & \adjustbox{angle=90}{\shortstack{2.23e+02\\{\scriptsize$\pm$3.09e+00}}} & \adjustbox{angle=90}{\shortstack{2.29e+02\\{\scriptsize$\pm$8.11e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{2.15e+02\\{\scriptsize$\pm$1.41e+02}}} & \adjustbox{angle=90}{\shortstack{4.50e+02\\{\scriptsize$\pm$9.66e+00}}} & \adjustbox{angle=90}{\shortstack{3.97e+02\\{\scriptsize$\pm$1.36e+02}}} & \adjustbox{angle=90}{\shortstack{4.51e+02\\{\scriptsize$\pm$1.18e+02}}} & \adjustbox{angle=90}{\shortstack{3.39e+02\\{\scriptsize$\pm$1.34e+02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.36e+02}\\{\scriptsize$\pm$\textbf{1.24e+02}}}} & \adjustbox{angle=90}{\shortstack{3.47e+02\\{\scriptsize$\pm$1.81e+02}}} & \adjustbox{angle=90}{\shortstack{1.99e+02\\{\scriptsize$\pm$1.41e+02}}} & \adjustbox{angle=90}{\shortstack{3.89e+02\\{\scriptsize$\pm$1.24e+02}}} & \adjustbox{angle=90}{\shortstack{4.44e+02\\{\scriptsize$\pm$1.25e+02}}} & \adjustbox{angle=90}{\shortstack{3.92e+02\\{\scriptsize$\pm$1.22e+02}}} & \adjustbox{angle=90}{\shortstack{4.00e+02\\{\scriptsize$\pm$8.74e+01}}} & \adjustbox{angle=90}{\shortstack{4.57e+02\\{\scriptsize$\pm$2.48e+01}}} & \adjustbox{angle=90}{\shortstack{4.02e+02\\{\scriptsize$\pm$8.90e+01}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:generalizedSchafferN2}}} & 100 & \adjustbox{angle=90}{\shortstack{1.30e+00\\{\scriptsize$\pm$2.04e+00}}} & \adjustbox{angle=90}{\shortstack{1.84e+01\\{\scriptsize$\pm$1.66e+00}}} & \adjustbox{angle=90}{\shortstack{6.78e-01\\{\scriptsize$\pm$9.67e-01}}} & \adjustbox{angle=90}{\shortstack{7.55e-01\\{\scriptsize$\pm$1.03e+00}}} & \adjustbox{angle=90}{\shortstack{9.85e-01\\{\scriptsize$\pm$1.71e+00}}} & \adjustbox{angle=90}{\shortstack{6.10e-01\\{\scriptsize$\pm$8.62e-01}}} & \adjustbox{angle=90}{\shortstack{6.35e-01\\{\scriptsize$\pm$1.16e+00}}} & \adjustbox{angle=90}{\shortstack{8.66e-01\\{\scriptsize$\pm$1.01e+00}}} & \adjustbox{angle=90}{\shortstack{1.71e+00\\{\scriptsize$\pm$2.76e+00}}} & \adjustbox{angle=90}{\shortstack{5.70e-01\\{\scriptsize$\pm$1.04e+00}}} & \adjustbox{angle=90}{\shortstack{9.63e-01\\{\scriptsize$\pm$1.23e+00}}} & \adjustbox{angle=90}{\shortstack{1.70e+00\\{\scriptsize$\pm$2.12e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{4.09e-03}\\{\scriptsize$\pm$\textbf{1.18e-02}}}} & \adjustbox{angle=90}{\shortstack{5.89e-01\\{\scriptsize$\pm$7.20e-01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{3.75e+00\\{\scriptsize$\pm$5.92e+00}}} & \adjustbox{angle=90}{\shortstack{1.13e+02\\{\scriptsize$\pm$7.22e+00}}} & \adjustbox{angle=90}{\shortstack{2.26e+00\\{\scriptsize$\pm$3.04e+00}}} & \adjustbox{angle=90}{\shortstack{1.92e+00\\{\scriptsize$\pm$3.96e+00}}} & \adjustbox{angle=90}{\shortstack{2.71e+00\\{\scriptsize$\pm$3.18e+00}}} & \adjustbox{angle=90}{\shortstack{2.36e+00\\{\scriptsize$\pm$2.86e+00}}} & \adjustbox{angle=90}{\shortstack{3.73e+00\\{\scriptsize$\pm$4.99e+00}}} & \adjustbox{angle=90}{\shortstack{4.29e+00\\{\scriptsize$\pm$7.10e+00}}} & \adjustbox{angle=90}{\shortstack{4.05e+00\\{\scriptsize$\pm$7.44e+00}}} & \adjustbox{angle=90}{\shortstack{2.26e+00\\{\scriptsize$\pm$6.63e+00}}} & \adjustbox{angle=90}{\shortstack{3.03e+00\\{\scriptsize$\pm$3.93e+00}}} & \adjustbox{angle=90}{\shortstack{4.08e+00\\{\scriptsize$\pm$4.45e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.43e-01}\\{\scriptsize$\pm$\textbf{5.96e-01}}}} & \adjustbox{angle=90}{\shortstack{5.02e+00\\{\scriptsize$\pm$6.33e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{4.78e+00\\{\scriptsize$\pm$7.70e+00}}} & \adjustbox{angle=90}{\shortstack{2.38e+02\\{\scriptsize$\pm$1.08e+01}}} & \adjustbox{angle=90}{\shortstack{3.38e+00\\{\scriptsize$\pm$4.67e+00}}} & \adjustbox{angle=90}{\shortstack{3.55e+00\\{\scriptsize$\pm$5.73e+00}}} & \adjustbox{angle=90}{\shortstack{6.20e+00\\{\scriptsize$\pm$5.75e+00}}} & \adjustbox{angle=90}{\shortstack{6.38e+00\\{\scriptsize$\pm$1.00e+01}}} & \adjustbox{angle=90}{\shortstack{5.55e+00\\{\scriptsize$\pm$6.35e+00}}} & \adjustbox{angle=90}{\shortstack{5.47e+00\\{\scriptsize$\pm$7.52e+00}}} & \adjustbox{angle=90}{\shortstack{5.68e+00\\{\scriptsize$\pm$6.41e+00}}} & \adjustbox{angle=90}{\shortstack{1.55e+00\\{\scriptsize$\pm$1.79e+00}}} & \adjustbox{angle=90}{\shortstack{4.54e+00\\{\scriptsize$\pm$5.27e+00}}} & \adjustbox{angle=90}{\shortstack{9.93e+00\\{\scriptsize$\pm$1.05e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{6.77e-01}\\{\scriptsize$\pm$\textbf{1.68e+00}}}} & \adjustbox{angle=90}{\shortstack{5.43e+00\\{\scriptsize$\pm$7.23e+00}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:generalizedSchafferN3}}} & 100 & \adjustbox{angle=90}{\shortstack{6.56e+01\\{\scriptsize$\pm$1.84e+01}}} & \adjustbox{angle=90}{\shortstack{3.11e+02\\{\scriptsize$\pm$1.72e+01}}} & \adjustbox{angle=90}{\shortstack{4.46e+01\\{\scriptsize$\pm$2.75e+01}}} & \adjustbox{angle=90}{\shortstack{5.23e+01\\{\scriptsize$\pm$2.07e+01}}} & \adjustbox{angle=90}{\shortstack{5.44e+01\\{\scriptsize$\pm$1.81e+01}}} & \adjustbox{angle=90}{\shortstack{5.16e+01\\{\scriptsize$\pm$2.23e+01}}} & \adjustbox{angle=90}{\shortstack{4.12e+01\\{\scriptsize$\pm$1.34e+01}}} & \adjustbox{angle=90}{\shortstack{4.96e+01\\{\scriptsize$\pm$1.43e+01}}} & \adjustbox{angle=90}{\shortstack{5.49e+01\\{\scriptsize$\pm$1.98e+01}}} & \adjustbox{angle=90}{\shortstack{5.06e+01\\{\scriptsize$\pm$1.68e+01}}} & \adjustbox{angle=90}{\shortstack{5.37e+01\\{\scriptsize$\pm$1.75e+01}}} & \adjustbox{angle=90}{\shortstack{2.58e+01\\{\scriptsize$\pm$1.01e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.94e+01}\\{\scriptsize$\pm$\textbf{9.51e+00}}}} & \adjustbox{angle=90}{\shortstack{4.35e+01\\{\scriptsize$\pm$1.19e+01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{3.16e+02\\{\scriptsize$\pm$1.01e+02}}} & \adjustbox{angle=90}{\shortstack{1.74e+03\\{\scriptsize$\pm$6.42e+01}}} & \adjustbox{angle=90}{\shortstack{2.24e+02\\{\scriptsize$\pm$8.80e+01}}} & \adjustbox{angle=90}{\shortstack{2.36e+02\\{\scriptsize$\pm$6.66e+01}}} & \adjustbox{angle=90}{\shortstack{2.78e+02\\{\scriptsize$\pm$6.88e+01}}} & \adjustbox{angle=90}{\shortstack{2.95e+02\\{\scriptsize$\pm$8.08e+01}}} & \adjustbox{angle=90}{\shortstack{1.99e+02\\{\scriptsize$\pm$7.00e+01}}} & \adjustbox{angle=90}{\shortstack{2.57e+02\\{\scriptsize$\pm$8.31e+01}}} & \adjustbox{angle=90}{\shortstack{3.03e+02\\{\scriptsize$\pm$7.85e+01}}} & \adjustbox{angle=90}{\shortstack{2.28e+02\\{\scriptsize$\pm$7.42e+01}}} & \adjustbox{angle=90}{\shortstack{2.75e+02\\{\scriptsize$\pm$1.00e+02}}} & \adjustbox{angle=90}{\shortstack{1.24e+02\\{\scriptsize$\pm$5.50e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{9.10e+01}\\{\scriptsize$\pm$\textbf{2.78e+01}}}} & \adjustbox{angle=90}{\shortstack{2.25e+02\\{\scriptsize$\pm$5.91e+01}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{5.40e+02\\{\scriptsize$\pm$1.79e+02}}} & \adjustbox{angle=90}{\shortstack{3.54e+03\\{\scriptsize$\pm$1.55e+02}}} & \adjustbox{angle=90}{\shortstack{4.84e+02\\{\scriptsize$\pm$1.73e+02}}} & \adjustbox{angle=90}{\shortstack{4.86e+02\\{\scriptsize$\pm$1.66e+02}}} & \adjustbox{angle=90}{\shortstack{5.29e+02\\{\scriptsize$\pm$1.75e+02}}} & \adjustbox{angle=90}{\shortstack{5.65e+02\\{\scriptsize$\pm$1.56e+02}}} & \adjustbox{angle=90}{\shortstack{4.23e+02\\{\scriptsize$\pm$1.56e+02}}} & \adjustbox{angle=90}{\shortstack{4.86e+02\\{\scriptsize$\pm$1.17e+02}}} & \adjustbox{angle=90}{\shortstack{5.61e+02\\{\scriptsize$\pm$1.51e+02}}} & \adjustbox{angle=90}{\shortstack{4.86e+02\\{\scriptsize$\pm$1.72e+02}}} & \adjustbox{angle=90}{\shortstack{5.35e+02\\{\scriptsize$\pm$1.86e+02}}} & \adjustbox{angle=90}{\shortstack{2.48e+02\\{\scriptsize$\pm$1.06e+02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.88e+02}\\{\scriptsize$\pm$\textbf{6.43e+01}}}} & \adjustbox{angle=90}{\shortstack{4.72e+02\\{\scriptsize$\pm$3.42e+02}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:generalizedSchafferN4}}} & 100 & \adjustbox{angle=90}{\shortstack{4.11e+00\\{\scriptsize$\pm$4.44e+00}}} & \adjustbox{angle=90}{\shortstack{3.97e+01\\{\scriptsize$\pm$3.40e+00}}} & \adjustbox{angle=90}{\shortstack{5.33e+00\\{\scriptsize$\pm$7.29e+00}}} & \adjustbox{angle=90}{\shortstack{5.39e+00\\{\scriptsize$\pm$6.64e+00}}} & \adjustbox{angle=90}{\shortstack{5.18e+00\\{\scriptsize$\pm$5.33e+00}}} & \adjustbox{angle=90}{\shortstack{4.74e+00\\{\scriptsize$\pm$5.76e+00}}} & \adjustbox{angle=90}{\shortstack{3.56e+00\\{\scriptsize$\pm$5.47e+00}}} & \adjustbox{angle=90}{\shortstack{5.53e+00\\{\scriptsize$\pm$9.02e+00}}} & \adjustbox{angle=90}{\shortstack{3.78e+00\\{\scriptsize$\pm$5.04e+00}}} & \adjustbox{angle=90}{\shortstack{3.19e+00\\{\scriptsize$\pm$4.23e+00}}} & \adjustbox{angle=90}{\shortstack{6.14e+00\\{\scriptsize$\pm$6.88e+00}}} & \adjustbox{angle=90}{\shortstack{3.87e-01\\{\scriptsize$\pm$8.01e-01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{8.01e-02}\\{\scriptsize$\pm$\textbf{5.60e-01}}}} & \adjustbox{angle=90}{\shortstack{2.30e+00\\{\scriptsize$\pm$5.12e+00}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{5.61e+00\\{\scriptsize$\pm$6.51e+00}}} & \adjustbox{angle=90}{\shortstack{2.04e+02\\{\scriptsize$\pm$1.21e+01}}} & \adjustbox{angle=90}{\shortstack{1.15e+01\\{\scriptsize$\pm$1.80e+01}}} & \adjustbox{angle=90}{\shortstack{7.46e+00\\{\scriptsize$\pm$1.21e+01}}} & \adjustbox{angle=90}{\shortstack{1.26e+01\\{\scriptsize$\pm$1.99e+01}}} & \adjustbox{angle=90}{\shortstack{1.72e+01\\{\scriptsize$\pm$3.43e+01}}} & \adjustbox{angle=90}{\shortstack{6.20e+00\\{\scriptsize$\pm$8.88e+00}}} & \adjustbox{angle=90}{\shortstack{1.98e+01\\{\scriptsize$\pm$3.93e+01}}} & \adjustbox{angle=90}{\shortstack{7.98e+00\\{\scriptsize$\pm$9.49e+00}}} & \adjustbox{angle=90}{\shortstack{4.34e+00\\{\scriptsize$\pm$7.16e+00}}} & \adjustbox{angle=90}{\shortstack{1.69e+01\\{\scriptsize$\pm$2.00e+01}}} & \adjustbox{angle=90}{\shortstack{6.50e-01\\{\scriptsize$\pm$1.87e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.06e-02}\\{\scriptsize$\pm$\textbf{5.04e-02}}}} & \adjustbox{angle=90}{\shortstack{5.33e+00\\{\scriptsize$\pm$1.12e+01}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{7.28e+00\\{\scriptsize$\pm$1.26e+01}}} & \adjustbox{angle=90}{\shortstack{4.06e+02\\{\scriptsize$\pm$2.38e+01}}} & \adjustbox{angle=90}{\shortstack{1.96e+01\\{\scriptsize$\pm$1.84e+01}}} & \adjustbox{angle=90}{\shortstack{1.45e+01\\{\scriptsize$\pm$2.48e+01}}} & \adjustbox{angle=90}{\shortstack{1.42e+01\\{\scriptsize$\pm$2.53e+01}}} & \adjustbox{angle=90}{\shortstack{2.05e+01\\{\scriptsize$\pm$3.56e+01}}} & \adjustbox{angle=90}{\shortstack{8.76e+00\\{\scriptsize$\pm$1.09e+01}}} & \adjustbox{angle=90}{\shortstack{2.08e+01\\{\scriptsize$\pm$4.51e+01}}} & \adjustbox{angle=90}{\shortstack{1.28e+01\\{\scriptsize$\pm$1.49e+01}}} & \adjustbox{angle=90}{\shortstack{1.16e+01\\{\scriptsize$\pm$3.73e+01}}} & \adjustbox{angle=90}{\shortstack{2.76e+01\\{\scriptsize$\pm$3.93e+01}}} & \adjustbox{angle=90}{\shortstack{1.63e+00\\{\scriptsize$\pm$7.14e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{7.11e-02}\\{\scriptsize$\pm$\textbf{2.06e-01}}}} & \adjustbox{angle=90}{\shortstack{1.01e+01\\{\scriptsize$\pm$3.20e+01}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:generalizedSchmidtVetters}}} & 100 & \adjustbox{angle=90}{\shortstack{6.47e+01\\{\scriptsize$\pm$2.96e+00}}} & \adjustbox{angle=90}{\shortstack{6.24e+01\\{\scriptsize$\pm$2.84e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{4.60e+01}\\{\scriptsize$\pm$\textbf{2.28e+01}}}} & \adjustbox{angle=90}{\shortstack{5.99e+01\\{\scriptsize$\pm$1.14e+01}}} & \adjustbox{angle=90}{\shortstack{6.27e+01\\{\scriptsize$\pm$4.83e+00}}} & \adjustbox{angle=90}{\shortstack{5.69e+01\\{\scriptsize$\pm$1.10e+01}}} & \adjustbox{angle=90}{\shortstack{5.86e+01\\{\scriptsize$\pm$9.43e+00}}} & \adjustbox{angle=90}{\shortstack{6.02e+01\\{\scriptsize$\pm$1.17e+01}}} & \adjustbox{angle=90}{\shortstack{6.31e+01\\{\scriptsize$\pm$3.52e+00}}} & \adjustbox{angle=90}{\shortstack{5.33e+01\\{\scriptsize$\pm$1.57e+01}}} & \adjustbox{angle=90}{\shortstack{6.11e+01\\{\scriptsize$\pm$7.69e+00}}} & \adjustbox{angle=90}{\shortstack{6.49e+01\\{\scriptsize$\pm$2.11e+00}}} & \adjustbox{angle=90}{\shortstack{6.33e+01\\{\scriptsize$\pm$1.54e+00}}} & \adjustbox{angle=90}{\shortstack{6.65e+01\\{\scriptsize$\pm$1.44e+00}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{3.38e+02\\{\scriptsize$\pm$3.38e+01}}} & \adjustbox{angle=90}{\shortstack{3.50e+02\\{\scriptsize$\pm$5.26e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.08e+02}\\{\scriptsize$\pm$\textbf{1.11e+02}}}} & \adjustbox{angle=90}{\shortstack{2.69e+02\\{\scriptsize$\pm$1.02e+02}}} & \adjustbox{angle=90}{\shortstack{3.16e+02\\{\scriptsize$\pm$7.54e+01}}} & \adjustbox{angle=90}{\shortstack{2.49e+02\\{\scriptsize$\pm$9.92e+01}}} & \adjustbox{angle=90}{\shortstack{2.73e+02\\{\scriptsize$\pm$9.55e+01}}} & \adjustbox{angle=90}{\shortstack{2.80e+02\\{\scriptsize$\pm$1.02e+02}}} & \adjustbox{angle=90}{\shortstack{3.20e+02\\{\scriptsize$\pm$6.53e+01}}} & \adjustbox{angle=90}{\shortstack{2.37e+02\\{\scriptsize$\pm$1.04e+02}}} & \adjustbox{angle=90}{\shortstack{2.90e+02\\{\scriptsize$\pm$1.02e+02}}} & \adjustbox{angle=90}{\shortstack{3.53e+02\\{\scriptsize$\pm$4.21e+00}}} & \adjustbox{angle=90}{\shortstack{3.51e+02\\{\scriptsize$\pm$3.19e+00}}} & \adjustbox{angle=90}{\shortstack{3.57e+02\\{\scriptsize$\pm$3.77e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{6.66e+02\\{\scriptsize$\pm$1.31e+02}}} & \adjustbox{angle=90}{\shortstack{7.16e+02\\{\scriptsize$\pm$6.69e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{4.22e+02}\\{\scriptsize$\pm$\textbf{2.36e+02}}}} & \adjustbox{angle=90}{\shortstack{4.93e+02\\{\scriptsize$\pm$1.96e+02}}} & \adjustbox{angle=90}{\shortstack{6.08e+02\\{\scriptsize$\pm$1.50e+02}}} & \adjustbox{angle=90}{\shortstack{4.34e+02\\{\scriptsize$\pm$2.47e+02}}} & \adjustbox{angle=90}{\shortstack{4.85e+02\\{\scriptsize$\pm$2.17e+02}}} & \adjustbox{angle=90}{\shortstack{5.65e+02\\{\scriptsize$\pm$1.76e+02}}} & \adjustbox{angle=90}{\shortstack{5.49e+02\\{\scriptsize$\pm$2.20e+02}}} & \adjustbox{angle=90}{\shortstack{4.45e+02\\{\scriptsize$\pm$2.15e+02}}} & \adjustbox{angle=90}{\shortstack{6.06e+02\\{\scriptsize$\pm$1.74e+02}}} & \adjustbox{angle=90}{\shortstack{7.20e+02\\{\scriptsize$\pm$5.95e+00}}} & \adjustbox{angle=90}{\shortstack{7.16e+02\\{\scriptsize$\pm$4.63e+00}}} & \adjustbox{angle=90}{\shortstack{7.24e+02\\{\scriptsize$\pm$5.18e+00}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:lennardJonesMinimumEnergyCluster}}} & 100 & \adjustbox{angle=90}{\shortstack{3.80e+00\\{\scriptsize$\pm$3.46e+00}}} & \adjustbox{angle=90}{\shortstack{7.20e+00\\{\scriptsize$\pm$3.11e+00}}} & \adjustbox{angle=90}{\shortstack{-7.80e-01\\{\scriptsize$\pm$3.91e+00}}} & \adjustbox{angle=90}{\shortstack{7.66e-01\\{\scriptsize$\pm$3.52e+00}}} & \adjustbox{angle=90}{\shortstack{-1.52e-01\\{\scriptsize$\pm$3.78e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-5.42e+00}\\{\scriptsize$\pm$\textbf{3.39e+00}}}} & \adjustbox{angle=90}{\shortstack{-1.58e-01\\{\scriptsize$\pm$4.48e+00}}} & \adjustbox{angle=90}{\shortstack{-3.87e+00\\{\scriptsize$\pm$5.65e+00}}} & \adjustbox{angle=90}{\shortstack{1.17e+00\\{\scriptsize$\pm$4.38e+00}}} & \adjustbox{angle=90}{\shortstack{1.78e+00\\{\scriptsize$\pm$3.56e+00}}} & \adjustbox{angle=90}{\shortstack{1.84e-01\\{\scriptsize$\pm$4.64e+00}}} & \adjustbox{angle=90}{\shortstack{3.03e+00\\{\scriptsize$\pm$5.00e+00}}} & \adjustbox{angle=90}{\shortstack{-1.14e+00\\{\scriptsize$\pm$5.21e+00}}} & \adjustbox{angle=90}{\shortstack{1.98e+00\\{\scriptsize$\pm$4.29e+00}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{-2.93e-01\\{\scriptsize$\pm$5.15e+00}}} & \adjustbox{angle=90}{\shortstack{-2.48e-01\\{\scriptsize$\pm$9.04e+00}}} & \adjustbox{angle=90}{\shortstack{-1.30e+01\\{\scriptsize$\pm$1.12e+01}}} & \adjustbox{angle=90}{\shortstack{-7.45e+00\\{\scriptsize$\pm$8.29e+00}}} & \adjustbox{angle=90}{\shortstack{-5.93e+00\\{\scriptsize$\pm$6.33e+00}}} & \adjustbox{angle=90}{\shortstack{-1.92e+01\\{\scriptsize$\pm$9.64e+00}}} & \adjustbox{angle=90}{\shortstack{-1.11e+01\\{\scriptsize$\pm$9.17e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-2.11e+01}\\{\scriptsize$\pm$\textbf{8.60e+00}}}} & \adjustbox{angle=90}{\shortstack{-5.64e+00\\{\scriptsize$\pm$6.49e+00}}} & \adjustbox{angle=90}{\shortstack{-4.40e+00\\{\scriptsize$\pm$6.94e+00}}} & \adjustbox{angle=90}{\shortstack{-9.75e+00\\{\scriptsize$\pm$8.54e+00}}} & \adjustbox{angle=90}{\shortstack{-5.40e+00\\{\scriptsize$\pm$1.18e+01}}} & \adjustbox{angle=90}{\shortstack{-1.43e+01\\{\scriptsize$\pm$1.06e+01}}} & \adjustbox{angle=90}{\shortstack{-1.26e+01\\{\scriptsize$\pm$9.29e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{-2.56e+00\\{\scriptsize$\pm$4.15e+00}}} & \adjustbox{angle=90}{\shortstack{-1.95e+00\\{\scriptsize$\pm$8.84e+00}}} & \adjustbox{angle=90}{\shortstack{-1.80e+01\\{\scriptsize$\pm$8.63e+00}}} & \adjustbox{angle=90}{\shortstack{-9.83e+00\\{\scriptsize$\pm$9.24e+00}}} & \adjustbox{angle=90}{\shortstack{-1.14e+01\\{\scriptsize$\pm$7.93e+00}}} & \adjustbox{angle=90}{\shortstack{-2.17e+01\\{\scriptsize$\pm$8.88e+00}}} & \adjustbox{angle=90}{\shortstack{-1.58e+01\\{\scriptsize$\pm$1.10e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-2.29e+01}\\{\scriptsize$\pm$\textbf{8.31e+00}}}} & \adjustbox{angle=90}{\shortstack{-8.90e+00\\{\scriptsize$\pm$7.34e+00}}} & \adjustbox{angle=90}{\shortstack{-1.01e+01\\{\scriptsize$\pm$1.00e+01}}} & \adjustbox{angle=90}{\shortstack{-1.20e+01\\{\scriptsize$\pm$9.15e+00}}} & \adjustbox{angle=90}{\shortstack{-1.46e+01\\{\scriptsize$\pm$1.10e+01}}} & \adjustbox{angle=90}{\shortstack{-1.84e+01\\{\scriptsize$\pm$8.39e+00}}} & \adjustbox{angle=90}{\shortstack{-1.66e+01\\{\scriptsize$\pm$8.36e+00}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:michalewicz}}} & 100 & \adjustbox{angle=90}{\shortstack{-2.83e+01\\{\scriptsize$\pm$1.84e+00}}} & \adjustbox{angle=90}{\shortstack{-3.05e+01\\{\scriptsize$\pm$2.23e+00}}} & \adjustbox{angle=90}{\shortstack{-3.13e+01\\{\scriptsize$\pm$2.34e+00}}} & \adjustbox{angle=90}{\shortstack{-3.07e+01\\{\scriptsize$\pm$2.55e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-3.19e+01}\\{\scriptsize$\pm$\textbf{2.88e+00}}}} & \adjustbox{angle=90}{\shortstack{-2.91e+01\\{\scriptsize$\pm$2.51e+00}}} & \adjustbox{angle=90}{\shortstack{-3.12e+01\\{\scriptsize$\pm$2.74e+00}}} & \adjustbox{angle=90}{\shortstack{-3.09e+01\\{\scriptsize$\pm$2.68e+00}}} & \adjustbox{angle=90}{\shortstack{-2.98e+01\\{\scriptsize$\pm$2.44e+00}}} & \adjustbox{angle=90}{\shortstack{-2.83e+01\\{\scriptsize$\pm$1.74e+00}}} & \adjustbox{angle=90}{\shortstack{-2.96e+01\\{\scriptsize$\pm$2.50e+00}}} & \adjustbox{angle=90}{\shortstack{-3.02e+01\\{\scriptsize$\pm$1.94e+00}}} & \adjustbox{angle=90}{\shortstack{-3.01e+01\\{\scriptsize$\pm$1.69e+00}}} & \adjustbox{angle=90}{\shortstack{-2.84e+01\\{\scriptsize$\pm$1.96e+00}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{-1.07e+02\\{\scriptsize$\pm$2.75e+00}}} & \adjustbox{angle=90}{\shortstack{-1.06e+02\\{\scriptsize$\pm$2.77e+00}}} & \adjustbox{angle=90}{\shortstack{-1.12e+02\\{\scriptsize$\pm$6.33e+00}}} & \adjustbox{angle=90}{\shortstack{-1.10e+02\\{\scriptsize$\pm$4.29e+00}}} & \adjustbox{angle=90}{\shortstack{-1.12e+02\\{\scriptsize$\pm$5.04e+00}}} & \adjustbox{angle=90}{\shortstack{-1.11e+02\\{\scriptsize$\pm$4.08e+00}}} & \adjustbox{angle=90}{\shortstack{-1.13e+02\\{\scriptsize$\pm$5.04e+00}}} & \adjustbox{angle=90}{\shortstack{-1.13e+02\\{\scriptsize$\pm$4.89e+00}}} & \adjustbox{angle=90}{\shortstack{-1.10e+02\\{\scriptsize$\pm$3.96e+00}}} & \adjustbox{angle=90}{\shortstack{-1.09e+02\\{\scriptsize$\pm$2.94e+00}}} & \adjustbox{angle=90}{\shortstack{-1.10e+02\\{\scriptsize$\pm$3.12e+00}}} & \adjustbox{angle=90}{\shortstack{-1.12e+02\\{\scriptsize$\pm$3.88e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-1.18e+02}\\{\scriptsize$\pm$\textbf{8.56e+00}}}} & \adjustbox{angle=90}{\shortstack{-1.09e+02\\{\scriptsize$\pm$3.50e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{-2.04e+02\\{\scriptsize$\pm$4.50e+00}}} & \adjustbox{angle=90}{\shortstack{-1.97e+02\\{\scriptsize$\pm$3.89e+00}}} & \adjustbox{angle=90}{\shortstack{-2.10e+02\\{\scriptsize$\pm$5.50e+00}}} & \adjustbox{angle=90}{\shortstack{-2.08e+02\\{\scriptsize$\pm$5.16e+00}}} & \adjustbox{angle=90}{\shortstack{-2.10e+02\\{\scriptsize$\pm$6.15e+00}}} & \adjustbox{angle=90}{\shortstack{-2.04e+02\\{\scriptsize$\pm$5.04e+00}}} & \adjustbox{angle=90}{\shortstack{-2.10e+02\\{\scriptsize$\pm$5.66e+00}}} & \adjustbox{angle=90}{\shortstack{-2.07e+02\\{\scriptsize$\pm$5.89e+00}}} & \adjustbox{angle=90}{\shortstack{-2.05e+02\\{\scriptsize$\pm$5.02e+00}}} & \adjustbox{angle=90}{\shortstack{-2.03e+02\\{\scriptsize$\pm$4.70e+00}}} & \adjustbox{angle=90}{\shortstack{-2.06e+02\\{\scriptsize$\pm$4.59e+00}}} & \adjustbox{angle=90}{\shortstack{-2.10e+02\\{\scriptsize$\pm$6.23e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-2.15e+02}\\{\scriptsize$\pm$\textbf{1.33e+01}}}} & \adjustbox{angle=90}{\shortstack{-2.07e+02\\{\scriptsize$\pm$4.81e+00}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:Mishra03}}} & 100 & \adjustbox{angle=90}{\shortstack{-4.02e+00\\{\scriptsize$\pm$6.42e-01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-4.46e+00}\\{\scriptsize$\pm$\textbf{6.05e-01}}}} & \adjustbox{angle=90}{\shortstack{-3.56e+00\\{\scriptsize$\pm$6.62e-01}}} & \adjustbox{angle=90}{\shortstack{-3.72e+00\\{\scriptsize$\pm$6.60e-01}}} & \adjustbox{angle=90}{\shortstack{-3.68e+00\\{\scriptsize$\pm$6.39e-01}}} & \adjustbox{angle=90}{\shortstack{-3.33e+00\\{\scriptsize$\pm$7.37e-01}}} & \adjustbox{angle=90}{\shortstack{-3.84e+00\\{\scriptsize$\pm$6.11e-01}}} & \adjustbox{angle=90}{\shortstack{-3.69e+00\\{\scriptsize$\pm$6.18e-01}}} & \adjustbox{angle=90}{\shortstack{-3.94e+00\\{\scriptsize$\pm$5.49e-01}}} & \adjustbox{angle=90}{\shortstack{-3.61e+00\\{\scriptsize$\pm$5.04e-01}}} & \adjustbox{angle=90}{\shortstack{-3.65e+00\\{\scriptsize$\pm$5.46e-01}}} & \adjustbox{angle=90}{\shortstack{-4.02e+00\\{\scriptsize$\pm$6.73e-01}}} & \adjustbox{angle=90}{\shortstack{-4.03e+00\\{\scriptsize$\pm$4.94e-01}}} & \adjustbox{angle=90}{\shortstack{-4.44e+00\\{\scriptsize$\pm$6.88e-01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{-1.02e+01\\{\scriptsize$\pm$1.34e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-1.22e+01}\\{\scriptsize$\pm$\textbf{1.46e+00}}}} & \adjustbox{angle=90}{\shortstack{-9.45e+00\\{\scriptsize$\pm$1.11e+00}}} & \adjustbox{angle=90}{\shortstack{-9.65e+00\\{\scriptsize$\pm$1.09e+00}}} & \adjustbox{angle=90}{\shortstack{-9.27e+00\\{\scriptsize$\pm$1.34e+00}}} & \adjustbox{angle=90}{\shortstack{-9.04e+00\\{\scriptsize$\pm$1.34e+00}}} & \adjustbox{angle=90}{\shortstack{-1.08e+01\\{\scriptsize$\pm$1.46e+00}}} & \adjustbox{angle=90}{\shortstack{-1.08e+01\\{\scriptsize$\pm$1.40e+00}}} & \adjustbox{angle=90}{\shortstack{-9.70e+00\\{\scriptsize$\pm$1.33e+00}}} & \adjustbox{angle=90}{\shortstack{-9.52e+00\\{\scriptsize$\pm$1.08e+00}}} & \adjustbox{angle=90}{\shortstack{-9.96e+00\\{\scriptsize$\pm$1.37e+00}}} & \adjustbox{angle=90}{\shortstack{-1.05e+01\\{\scriptsize$\pm$1.18e+00}}} & \adjustbox{angle=90}{\shortstack{-1.02e+01\\{\scriptsize$\pm$1.25e+00}}} & \adjustbox{angle=90}{\shortstack{-1.17e+01\\{\scriptsize$\pm$1.24e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{-1.46e+01\\{\scriptsize$\pm$1.89e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-1.78e+01}\\{\scriptsize$\pm$\textbf{1.66e+00}}}} & \adjustbox{angle=90}{\shortstack{-1.32e+01\\{\scriptsize$\pm$1.74e+00}}} & \adjustbox{angle=90}{\shortstack{-1.39e+01\\{\scriptsize$\pm$1.78e+00}}} & \adjustbox{angle=90}{\shortstack{-1.36e+01\\{\scriptsize$\pm$1.48e+00}}} & \adjustbox{angle=90}{\shortstack{-1.31e+01\\{\scriptsize$\pm$1.92e+00}}} & \adjustbox{angle=90}{\shortstack{-1.47e+01\\{\scriptsize$\pm$2.03e+00}}} & \adjustbox{angle=90}{\shortstack{-1.53e+01\\{\scriptsize$\pm$1.98e+00}}} & \adjustbox{angle=90}{\shortstack{-1.41e+01\\{\scriptsize$\pm$1.45e+00}}} & \adjustbox{angle=90}{\shortstack{-1.35e+01\\{\scriptsize$\pm$1.65e+00}}} & \adjustbox{angle=90}{\shortstack{-1.39e+01\\{\scriptsize$\pm$1.43e+00}}} & \adjustbox{angle=90}{\shortstack{-1.49e+01\\{\scriptsize$\pm$1.82e+00}}} & \adjustbox{angle=90}{\shortstack{-1.44e+01\\{\scriptsize$\pm$1.90e+00}}} & \adjustbox{angle=90}{\shortstack{-1.72e+01\\{\scriptsize$\pm$1.84e+00}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:Mishra04}}} & 100 & \adjustbox{angle=90}{\shortstack{-4.03e+00\\{\scriptsize$\pm$6.50e-01}}} & \adjustbox{angle=90}{\shortstack{-4.40e+00\\{\scriptsize$\pm$6.75e-01}}} & \adjustbox{angle=90}{\shortstack{-3.56e+00\\{\scriptsize$\pm$7.09e-01}}} & \adjustbox{angle=90}{\shortstack{-3.75e+00\\{\scriptsize$\pm$6.55e-01}}} & \adjustbox{angle=90}{\shortstack{-3.65e+00\\{\scriptsize$\pm$7.36e-01}}} & \adjustbox{angle=90}{\shortstack{-3.48e+00\\{\scriptsize$\pm$5.84e-01}}} & \adjustbox{angle=90}{\shortstack{-4.30e+00\\{\scriptsize$\pm$5.87e-01}}} & \adjustbox{angle=90}{\shortstack{-3.87e+00\\{\scriptsize$\pm$7.66e-01}}} & \adjustbox{angle=90}{\shortstack{-4.05e+00\\{\scriptsize$\pm$5.74e-01}}} & \adjustbox{angle=90}{\shortstack{-3.83e+00\\{\scriptsize$\pm$6.57e-01}}} & \adjustbox{angle=90}{\shortstack{-3.75e+00\\{\scriptsize$\pm$5.87e-01}}} & \adjustbox{angle=90}{\shortstack{-4.08e+00\\{\scriptsize$\pm$6.74e-01}}} & \adjustbox{angle=90}{\shortstack{-4.05e+00\\{\scriptsize$\pm$5.07e-01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-4.66e+00}\\{\scriptsize$\pm$\textbf{6.18e-01}}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{-9.86e+00\\{\scriptsize$\pm$1.36e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-1.18e+01}\\{\scriptsize$\pm$\textbf{1.23e+00}}}} & \adjustbox{angle=90}{\shortstack{-9.14e+00\\{\scriptsize$\pm$1.24e+00}}} & \adjustbox{angle=90}{\shortstack{-9.06e+00\\{\scriptsize$\pm$1.31e+00}}} & \adjustbox{angle=90}{\shortstack{-9.62e+00\\{\scriptsize$\pm$1.28e+00}}} & \adjustbox{angle=90}{\shortstack{-9.21e+00\\{\scriptsize$\pm$1.18e+00}}} & \adjustbox{angle=90}{\shortstack{-9.83e+00\\{\scriptsize$\pm$1.60e+00}}} & \adjustbox{angle=90}{\shortstack{-1.02e+01\\{\scriptsize$\pm$1.65e+00}}} & \adjustbox{angle=90}{\shortstack{-9.87e+00\\{\scriptsize$\pm$1.38e+00}}} & \adjustbox{angle=90}{\shortstack{-9.69e+00\\{\scriptsize$\pm$9.73e-01}}} & \adjustbox{angle=90}{\shortstack{-9.54e+00\\{\scriptsize$\pm$1.13e+00}}} & \adjustbox{angle=90}{\shortstack{-1.03e+01\\{\scriptsize$\pm$1.64e+00}}} & \adjustbox{angle=90}{\shortstack{-1.01e+01\\{\scriptsize$\pm$1.27e+00}}} & \adjustbox{angle=90}{\shortstack{-1.14e+01\\{\scriptsize$\pm$1.46e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{-1.53e+01\\{\scriptsize$\pm$2.18e+00}}} & \adjustbox{angle=90}{\shortstack{-1.76e+01\\{\scriptsize$\pm$1.95e+00}}} & \adjustbox{angle=90}{\shortstack{-1.36e+01\\{\scriptsize$\pm$1.96e+00}}} & \adjustbox{angle=90}{\shortstack{-1.33e+01\\{\scriptsize$\pm$1.47e+00}}} & \adjustbox{angle=90}{\shortstack{-1.36e+01\\{\scriptsize$\pm$1.97e+00}}} & \adjustbox{angle=90}{\shortstack{-1.30e+01\\{\scriptsize$\pm$1.64e+00}}} & \adjustbox{angle=90}{\shortstack{-1.67e+01\\{\scriptsize$\pm$2.51e+00}}} & \adjustbox{angle=90}{\shortstack{-1.67e+01\\{\scriptsize$\pm$2.64e+00}}} & \adjustbox{angle=90}{\shortstack{-1.43e+01\\{\scriptsize$\pm$1.54e+00}}} & \adjustbox{angle=90}{\shortstack{-1.39e+01\\{\scriptsize$\pm$1.74e+00}}} & \adjustbox{angle=90}{\shortstack{-1.41e+01\\{\scriptsize$\pm$1.74e+00}}} & \adjustbox{angle=90}{\shortstack{-1.47e+01\\{\scriptsize$\pm$2.02e+00}}} & \adjustbox{angle=90}{\shortstack{-1.46e+01\\{\scriptsize$\pm$2.13e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-1.77e+01}\\{\scriptsize$\pm$\textbf{1.96e+00}}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:RotatedBentCigar}}} & 100 & \adjustbox{angle=90}{\shortstack{9.01e+06\\{\scriptsize$\pm$1.12e+07}}} & \adjustbox{angle=90}{\shortstack{3.99e+09\\{\scriptsize$\pm$9.49e+08}}} & \adjustbox{angle=90}{\shortstack{9.71e+05\\{\scriptsize$\pm$9.98e+05}}} & \adjustbox{angle=90}{\shortstack{2.01e+08\\{\scriptsize$\pm$1.38e+09}}} & \adjustbox{angle=90}{\shortstack{4.29e+06\\{\scriptsize$\pm$3.94e+06}}} & \adjustbox{angle=90}{\shortstack{2.79e+06\\{\scriptsize$\pm$3.22e+06}}} & \adjustbox{angle=90}{\shortstack{9.33e+05\\{\scriptsize$\pm$1.35e+06}}} & \adjustbox{angle=90}{\shortstack{3.09e+06\\{\scriptsize$\pm$5.71e+06}}} & \adjustbox{angle=90}{\shortstack{6.27e+06\\{\scriptsize$\pm$6.65e+06}}} & \adjustbox{angle=90}{\shortstack{3.69e+06\\{\scriptsize$\pm$3.80e+06}}} & \adjustbox{angle=90}{\shortstack{2.76e+06\\{\scriptsize$\pm$2.62e+06}}} & \adjustbox{angle=90}{\shortstack{6.49e+04\\{\scriptsize$\pm$1.09e+05}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.41e+04}\\{\scriptsize$\pm$\textbf{2.39e+04}}}} & \adjustbox{angle=90}{\shortstack{6.79e+05\\{\scriptsize$\pm$9.34e+05}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{1.36e+08\\{\scriptsize$\pm$5.06e+08}}} & \adjustbox{angle=90}{\shortstack{4.52e+10\\{\scriptsize$\pm$5.05e+09}}} & \adjustbox{angle=90}{\shortstack{4.04e+08\\{\scriptsize$\pm$1.90e+09}}} & \adjustbox{angle=90}{\shortstack{4.23e+08\\{\scriptsize$\pm$1.94e+09}}} & \adjustbox{angle=90}{\shortstack{2.39e+07\\{\scriptsize$\pm$2.91e+07}}} & \adjustbox{angle=90}{\shortstack{2.26e+08\\{\scriptsize$\pm$1.39e+09}}} & \adjustbox{angle=90}{\shortstack{5.86e+06\\{\scriptsize$\pm$2.08e+07}}} & \adjustbox{angle=90}{\shortstack{2.11e+07\\{\scriptsize$\pm$2.26e+07}}} & \adjustbox{angle=90}{\shortstack{4.94e+07\\{\scriptsize$\pm$4.23e+07}}} & \adjustbox{angle=90}{\shortstack{2.23e+08\\{\scriptsize$\pm$1.39e+09}}} & \adjustbox{angle=90}{\shortstack{1.91e+07\\{\scriptsize$\pm$3.32e+07}}} & \adjustbox{angle=90}{\shortstack{7.03e+05\\{\scriptsize$\pm$9.32e+05}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{7.04e+04}\\{\scriptsize$\pm$\textbf{8.98e+04}}}} & \adjustbox{angle=90}{\shortstack{3.12e+06\\{\scriptsize$\pm$4.22e+06}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{1.41e+08\\{\scriptsize$\pm$1.33e+08}}} & \adjustbox{angle=90}{\shortstack{9.89e+10\\{\scriptsize$\pm$1.12e+10}}} & \adjustbox{angle=90}{\shortstack{2.24e+08\\{\scriptsize$\pm$1.39e+09}}} & \adjustbox{angle=90}{\shortstack{2.05e+09\\{\scriptsize$\pm$8.90e+09}}} & \adjustbox{angle=90}{\shortstack{9.26e+07\\{\scriptsize$\pm$1.66e+08}}} & \adjustbox{angle=90}{\shortstack{1.01e+09\\{\scriptsize$\pm$4.46e+09}}} & \adjustbox{angle=90}{\shortstack{1.30e+07\\{\scriptsize$\pm$1.87e+07}}} & \adjustbox{angle=90}{\shortstack{3.62e+07\\{\scriptsize$\pm$3.68e+07}}} & \adjustbox{angle=90}{\shortstack{9.25e+07\\{\scriptsize$\pm$8.67e+07}}} & \adjustbox{angle=90}{\shortstack{4.52e+07\\{\scriptsize$\pm$1.01e+08}}} & \adjustbox{angle=90}{\shortstack{4.97e+07\\{\scriptsize$\pm$4.49e+07}}} & \adjustbox{angle=90}{\shortstack{1.06e+06\\{\scriptsize$\pm$1.48e+06}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.08e+05}\\{\scriptsize$\pm$\textbf{1.53e+05}}}} & \adjustbox{angle=90}{\shortstack{4.98e+06\\{\scriptsize$\pm$4.31e+06}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:RotatedDiscus}}} & 100 & \adjustbox{angle=90}{\shortstack{2.94e+04\\{\scriptsize$\pm$2.63e+04}}} & \adjustbox{angle=90}{\shortstack{3.45e+04\\{\scriptsize$\pm$7.18e+03}}} & \adjustbox{angle=90}{\shortstack{3.93e+04\\{\scriptsize$\pm$6.53e+04}}} & \adjustbox{angle=90}{\shortstack{4.17e+04\\{\scriptsize$\pm$6.18e+04}}} & \adjustbox{angle=90}{\shortstack{4.18e+04\\{\scriptsize$\pm$7.29e+04}}} & \adjustbox{angle=90}{\shortstack{7.11e+04\\{\scriptsize$\pm$8.53e+04}}} & \adjustbox{angle=90}{\shortstack{2.72e+04\\{\scriptsize$\pm$3.61e+04}}} & \adjustbox{angle=90}{\shortstack{2.28e+04\\{\scriptsize$\pm$2.77e+04}}} & \adjustbox{angle=90}{\shortstack{2.10e+04\\{\scriptsize$\pm$2.53e+04}}} & \adjustbox{angle=90}{\shortstack{5.59e+04\\{\scriptsize$\pm$5.96e+04}}} & \adjustbox{angle=90}{\shortstack{1.86e+04\\{\scriptsize$\pm$2.22e+04}}} & \adjustbox{angle=90}{\shortstack{3.49e+04\\{\scriptsize$\pm$2.46e+04}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.88e+03}\\{\scriptsize$\pm$\textbf{2.85e+03}}}} & \adjustbox{angle=90}{\shortstack{1.07e+05\\{\scriptsize$\pm$7.42e+04}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{6.47e+04\\{\scriptsize$\pm$6.77e+04}}} & \adjustbox{angle=90}{\shortstack{1.74e+05\\{\scriptsize$\pm$3.15e+04}}} & \adjustbox{angle=90}{\shortstack{6.07e+04\\{\scriptsize$\pm$7.08e+04}}} & \adjustbox{angle=90}{\shortstack{1.53e+05\\{\scriptsize$\pm$2.13e+05}}} & \adjustbox{angle=90}{\shortstack{4.89e+04\\{\scriptsize$\pm$6.62e+04}}} & \adjustbox{angle=90}{\shortstack{1.28e+05\\{\scriptsize$\pm$3.18e+05}}} & \adjustbox{angle=90}{\shortstack{3.67e+04\\{\scriptsize$\pm$1.07e+05}}} & \adjustbox{angle=90}{\shortstack{2.40e+04\\{\scriptsize$\pm$2.53e+04}}} & \adjustbox{angle=90}{\shortstack{5.31e+04\\{\scriptsize$\pm$1.06e+05}}} & \adjustbox{angle=90}{\shortstack{1.47e+05\\{\scriptsize$\pm$1.75e+05}}} & \adjustbox{angle=90}{\shortstack{5.02e+04\\{\scriptsize$\pm$8.25e+04}}} & \adjustbox{angle=90}{\shortstack{5.49e+04\\{\scriptsize$\pm$5.11e+04}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{4.21e+03}\\{\scriptsize$\pm$\textbf{9.13e+03}}}} & \adjustbox{angle=90}{\shortstack{3.18e+05\\{\scriptsize$\pm$2.27e+05}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{8.12e+04\\{\scriptsize$\pm$9.79e+04}}} & \adjustbox{angle=90}{\shortstack{3.41e+05\\{\scriptsize$\pm$7.22e+04}}} & \adjustbox{angle=90}{\shortstack{1.02e+05\\{\scriptsize$\pm$2.38e+05}}} & \adjustbox{angle=90}{\shortstack{8.87e+04\\{\scriptsize$\pm$1.23e+05}}} & \adjustbox{angle=90}{\shortstack{4.90e+04\\{\scriptsize$\pm$5.22e+04}}} & \adjustbox{angle=90}{\shortstack{2.24e+05\\{\scriptsize$\pm$3.87e+05}}} & \adjustbox{angle=90}{\shortstack{4.80e+04\\{\scriptsize$\pm$8.49e+04}}} & \adjustbox{angle=90}{\shortstack{3.44e+04\\{\scriptsize$\pm$6.15e+04}}} & \adjustbox{angle=90}{\shortstack{5.30e+04\\{\scriptsize$\pm$4.35e+04}}} & \adjustbox{angle=90}{\shortstack{1.55e+05\\{\scriptsize$\pm$2.04e+05}}} & \adjustbox{angle=90}{\shortstack{5.12e+04\\{\scriptsize$\pm$7.07e+04}}} & \adjustbox{angle=90}{\shortstack{8.43e+04\\{\scriptsize$\pm$1.05e+05}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{3.95e+03}\\{\scriptsize$\pm$\textbf{5.22e+03}}}} & \adjustbox{angle=90}{\shortstack{4.41e+05\\{\scriptsize$\pm$3.87e+05}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:RotatedHighConditionedElliptic}}} & 100 & \adjustbox{angle=90}{\shortstack{3.30e+05\\{\scriptsize$\pm$3.18e+05}}} & \adjustbox{angle=90}{\shortstack{5.66e+07\\{\scriptsize$\pm$2.47e+07}}} & \adjustbox{angle=90}{\shortstack{8.48e+06\\{\scriptsize$\pm$3.30e+07}}} & \adjustbox{angle=90}{\shortstack{1.06e+07\\{\scriptsize$\pm$4.33e+07}}} & \adjustbox{angle=90}{\shortstack{7.84e+06\\{\scriptsize$\pm$2.45e+07}}} & \adjustbox{angle=90}{\shortstack{1.22e+07\\{\scriptsize$\pm$3.29e+07}}} & \adjustbox{angle=90}{\shortstack{2.25e+06\\{\scriptsize$\pm$1.53e+07}}} & \adjustbox{angle=90}{\shortstack{3.74e+06\\{\scriptsize$\pm$2.46e+07}}} & \adjustbox{angle=90}{\shortstack{3.14e+06\\{\scriptsize$\pm$1.17e+07}}} & \adjustbox{angle=90}{\shortstack{7.96e+06\\{\scriptsize$\pm$2.86e+07}}} & \adjustbox{angle=90}{\shortstack{3.88e+06\\{\scriptsize$\pm$2.56e+07}}} & \adjustbox{angle=90}{\shortstack{3.72e+04\\{\scriptsize$\pm$5.59e+04}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.83e+03}\\{\scriptsize$\pm$\textbf{4.94e+03}}}} & \adjustbox{angle=90}{\shortstack{2.31e+05\\{\scriptsize$\pm$2.91e+05}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{4.36e+06\\{\scriptsize$\pm$3.79e+06}}} & \adjustbox{angle=90}{\shortstack{1.57e+09\\{\scriptsize$\pm$2.66e+08}}} & \adjustbox{angle=90}{\shortstack{3.47e+07\\{\scriptsize$\pm$1.69e+08}}} & \adjustbox{angle=90}{\shortstack{8.35e+07\\{\scriptsize$\pm$2.47e+08}}} & \adjustbox{angle=90}{\shortstack{1.90e+06\\{\scriptsize$\pm$2.24e+06}}} & \adjustbox{angle=90}{\shortstack{1.46e+07\\{\scriptsize$\pm$7.95e+07}}} & \adjustbox{angle=90}{\shortstack{1.09e+07\\{\scriptsize$\pm$7.26e+07}}} & \adjustbox{angle=90}{\shortstack{5.61e+06\\{\scriptsize$\pm$3.19e+07}}} & \adjustbox{angle=90}{\shortstack{3.00e+06\\{\scriptsize$\pm$2.55e+06}}} & \adjustbox{angle=90}{\shortstack{4.16e+07\\{\scriptsize$\pm$1.55e+08}}} & \adjustbox{angle=90}{\shortstack{1.93e+06\\{\scriptsize$\pm$2.29e+06}}} & \adjustbox{angle=90}{\shortstack{6.67e+04\\{\scriptsize$\pm$8.50e+04}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.03e+04}\\{\scriptsize$\pm$\textbf{1.98e+04}}}} & \adjustbox{angle=90}{\shortstack{5.09e+05\\{\scriptsize$\pm$5.29e+05}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{7.91e+06\\{\scriptsize$\pm$8.20e+06}}} & \adjustbox{angle=90}{\shortstack{4.57e+09\\{\scriptsize$\pm$5.68e+08}}} & \adjustbox{angle=90}{\shortstack{5.22e+07\\{\scriptsize$\pm$2.75e+08}}} & \adjustbox{angle=90}{\shortstack{8.87e+07\\{\scriptsize$\pm$2.91e+08}}} & \adjustbox{angle=90}{\shortstack{2.83e+07\\{\scriptsize$\pm$1.12e+08}}} & \adjustbox{angle=90}{\shortstack{1.31e+08\\{\scriptsize$\pm$6.82e+08}}} & \adjustbox{angle=90}{\shortstack{8.09e+05\\{\scriptsize$\pm$8.26e+05}}} & \adjustbox{angle=90}{\shortstack{2.81e+06\\{\scriptsize$\pm$2.79e+06}}} & \adjustbox{angle=90}{\shortstack{6.68e+06\\{\scriptsize$\pm$5.80e+06}}} & \adjustbox{angle=90}{\shortstack{7.53e+07\\{\scriptsize$\pm$2.67e+08}}} & \adjustbox{angle=90}{\shortstack{4.10e+06\\{\scriptsize$\pm$5.04e+06}}} & \adjustbox{angle=90}{\shortstack{1.40e+05\\{\scriptsize$\pm$1.60e+05}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.43e+04}\\{\scriptsize$\pm$\textbf{2.52e+04}}}} & \adjustbox{angle=90}{\shortstack{6.66e+05\\{\scriptsize$\pm$6.59e+05}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:Salomon}}} & 100 & \adjustbox{angle=90}{\shortstack{7.84e-01\\{\scriptsize$\pm$2.74e-01}}} & \adjustbox{angle=90}{\shortstack{1.00e+01\\{\scriptsize$\pm$7.34e-01}}} & \adjustbox{angle=90}{\shortstack{3.08e-01\\{\scriptsize$\pm$1.26e-01}}} & \adjustbox{angle=90}{\shortstack{4.71e-01\\{\scriptsize$\pm$1.99e-01}}} & \adjustbox{angle=90}{\shortstack{5.40e-01\\{\scriptsize$\pm$1.82e-01}}} & \adjustbox{angle=90}{\shortstack{5.01e-01\\{\scriptsize$\pm$2.50e-01}}} & \adjustbox{angle=90}{\shortstack{4.38e-01\\{\scriptsize$\pm$1.97e-01}}} & \adjustbox{angle=90}{\shortstack{4.88e-01\\{\scriptsize$\pm$2.15e-01}}} & \adjustbox{angle=90}{\shortstack{6.50e-01\\{\scriptsize$\pm$2.65e-01}}} & \adjustbox{angle=90}{\shortstack{5.56e-01\\{\scriptsize$\pm$2.17e-01}}} & \adjustbox{angle=90}{\shortstack{5.41e-01\\{\scriptsize$\pm$2.12e-01}}} & \adjustbox{angle=90}{\shortstack{3.74e-01\\{\scriptsize$\pm$2.19e-01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.63e-01}\\{\scriptsize$\pm$\textbf{1.50e-01}}}} & \adjustbox{angle=90}{\shortstack{4.32e-01\\{\scriptsize$\pm$1.51e-01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{1.32e+00\\{\scriptsize$\pm$6.52e-01}}} & \adjustbox{angle=90}{\shortstack{2.54e+01\\{\scriptsize$\pm$1.34e+00}}} & \adjustbox{angle=90}{\shortstack{1.27e+00\\{\scriptsize$\pm$2.63e+00}}} & \adjustbox{angle=90}{\shortstack{1.08e+00\\{\scriptsize$\pm$1.92e+00}}} & \adjustbox{angle=90}{\shortstack{1.52e+00\\{\scriptsize$\pm$2.29e+00}}} & \adjustbox{angle=90}{\shortstack{1.76e+00\\{\scriptsize$\pm$2.93e+00}}} & \adjustbox{angle=90}{\shortstack{7.21e-01\\{\scriptsize$\pm$3.03e-01}}} & \adjustbox{angle=90}{\shortstack{1.18e+00\\{\scriptsize$\pm$1.36e+00}}} & \adjustbox{angle=90}{\shortstack{1.19e+00\\{\scriptsize$\pm$5.71e-01}}} & \adjustbox{angle=90}{\shortstack{1.59e+00\\{\scriptsize$\pm$2.20e+00}}} & \adjustbox{angle=90}{\shortstack{9.84e-01\\{\scriptsize$\pm$1.34e+00}}} & \adjustbox{angle=90}{\shortstack{6.16e-01\\{\scriptsize$\pm$3.26e-01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{4.20e-01}\\{\scriptsize$\pm$\textbf{2.19e-01}}}} & \adjustbox{angle=90}{\shortstack{7.37e-01\\{\scriptsize$\pm$2.84e-01}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{1.57e+00\\{\scriptsize$\pm$6.11e-01}}} & \adjustbox{angle=90}{\shortstack{3.56e+01\\{\scriptsize$\pm$2.31e+00}}} & \adjustbox{angle=90}{\shortstack{2.55e+00\\{\scriptsize$\pm$4.23e+00}}} & \adjustbox{angle=90}{\shortstack{2.01e+00\\{\scriptsize$\pm$3.12e+00}}} & \adjustbox{angle=90}{\shortstack{1.54e+00\\{\scriptsize$\pm$1.32e+00}}} & \adjustbox{angle=90}{\shortstack{2.36e+00\\{\scriptsize$\pm$3.83e+00}}} & \adjustbox{angle=90}{\shortstack{9.38e-01\\{\scriptsize$\pm$4.64e-01}}} & \adjustbox{angle=90}{\shortstack{1.39e+00\\{\scriptsize$\pm$6.98e-01}}} & \adjustbox{angle=90}{\shortstack{1.80e+00\\{\scriptsize$\pm$1.19e+00}}} & \adjustbox{angle=90}{\shortstack{1.67e+00\\{\scriptsize$\pm$1.85e+00}}} & \adjustbox{angle=90}{\shortstack{1.64e+00\\{\scriptsize$\pm$1.86e+00}}} & \adjustbox{angle=90}{\shortstack{5.66e-01\\{\scriptsize$\pm$3.35e-01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{4.75e-01}\\{\scriptsize$\pm$\textbf{2.98e-01}}}} & \adjustbox{angle=90}{\shortstack{1.01e+00\\{\scriptsize$\pm$4.32e-01}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:SchwefelN20}}} & 100 & \adjustbox{angle=90}{\shortstack{1.60e+01\\{\scriptsize$\pm$2.31e+01}}} & \adjustbox{angle=90}{\shortstack{4.08e+01\\{\scriptsize$\pm$5.89e+00}}} & \adjustbox{angle=90}{\shortstack{1.93e+01\\{\scriptsize$\pm$2.42e+01}}} & \adjustbox{angle=90}{\shortstack{1.73e+01\\{\scriptsize$\pm$2.77e+01}}} & \adjustbox{angle=90}{\shortstack{1.70e+01\\{\scriptsize$\pm$2.47e+01}}} & \adjustbox{angle=90}{\shortstack{2.05e+01\\{\scriptsize$\pm$2.76e+01}}} & \adjustbox{angle=90}{\shortstack{7.38e+00\\{\scriptsize$\pm$1.79e+01}}} & \adjustbox{angle=90}{\shortstack{6.40e+00\\{\scriptsize$\pm$1.33e+01}}} & \adjustbox{angle=90}{\shortstack{1.30e+01\\{\scriptsize$\pm$1.95e+01}}} & \adjustbox{angle=90}{\shortstack{2.14e+01\\{\scriptsize$\pm$2.99e+01}}} & \adjustbox{angle=90}{\shortstack{1.52e+01\\{\scriptsize$\pm$2.36e+01}}} & \adjustbox{angle=90}{\shortstack{1.96e+00\\{\scriptsize$\pm$2.09e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{4.06e-01}\\{\scriptsize$\pm$\textbf{3.39e-01}}}} & \adjustbox{angle=90}{\shortstack{1.23e+01\\{\scriptsize$\pm$2.39e+01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{3.72e+01\\{\scriptsize$\pm$4.39e+01}}} & \adjustbox{angle=90}{\shortstack{1.04e+02\\{\scriptsize$\pm$1.44e+01}}} & \adjustbox{angle=90}{\shortstack{5.29e+01\\{\scriptsize$\pm$6.75e+01}}} & \adjustbox{angle=90}{\shortstack{5.58e+01\\{\scriptsize$\pm$6.59e+01}}} & \adjustbox{angle=90}{\shortstack{6.75e+01\\{\scriptsize$\pm$5.80e+01}}} & \adjustbox{angle=90}{\shortstack{5.89e+01\\{\scriptsize$\pm$6.48e+01}}} & \adjustbox{angle=90}{\shortstack{1.99e+01\\{\scriptsize$\pm$3.13e+01}}} & \adjustbox{angle=90}{\shortstack{2.04e+01\\{\scriptsize$\pm$3.32e+01}}} & \adjustbox{angle=90}{\shortstack{4.70e+01\\{\scriptsize$\pm$4.67e+01}}} & \adjustbox{angle=90}{\shortstack{6.41e+01\\{\scriptsize$\pm$5.96e+01}}} & \adjustbox{angle=90}{\shortstack{4.04e+01\\{\scriptsize$\pm$4.91e+01}}} & \adjustbox{angle=90}{\shortstack{5.99e+00\\{\scriptsize$\pm$5.97e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.06e+00}\\{\scriptsize$\pm$\textbf{9.34e-01}}}} & \adjustbox{angle=90}{\shortstack{3.31e+01\\{\scriptsize$\pm$4.37e+01}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{5.24e+01\\{\scriptsize$\pm$4.80e+01}}} & \adjustbox{angle=90}{\shortstack{1.57e+02\\{\scriptsize$\pm$2.53e+01}}} & \adjustbox{angle=90}{\shortstack{1.08e+02\\{\scriptsize$\pm$9.05e+01}}} & \adjustbox{angle=90}{\shortstack{6.46e+01\\{\scriptsize$\pm$6.89e+01}}} & \adjustbox{angle=90}{\shortstack{8.73e+01\\{\scriptsize$\pm$8.74e+01}}} & \adjustbox{angle=90}{\shortstack{9.75e+01\\{\scriptsize$\pm$1.07e+02}}} & \adjustbox{angle=90}{\shortstack{1.60e+01\\{\scriptsize$\pm$2.96e+01}}} & \adjustbox{angle=90}{\shortstack{4.07e+01\\{\scriptsize$\pm$5.86e+01}}} & \adjustbox{angle=90}{\shortstack{6.68e+01\\{\scriptsize$\pm$7.57e+01}}} & \adjustbox{angle=90}{\shortstack{9.64e+01\\{\scriptsize$\pm$7.15e+01}}} & \adjustbox{angle=90}{\shortstack{5.98e+01\\{\scriptsize$\pm$6.38e+01}}} & \adjustbox{angle=90}{\shortstack{9.33e+00\\{\scriptsize$\pm$9.46e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.52e+00}\\{\scriptsize$\pm$\textbf{1.40e+00}}}} & \adjustbox{angle=90}{\shortstack{5.00e+01\\{\scriptsize$\pm$5.50e+01}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:SchwefelN36}}} & 100 & \adjustbox{angle=90}{\shortstack{2.92e+10\\{\scriptsize$\pm$3.33e+09}}} & \adjustbox{angle=90}{\shortstack{2.76e+10\\{\scriptsize$\pm$2.64e+09}}} & \adjustbox{angle=90}{\shortstack{3.01e+10\\{\scriptsize$\pm$2.83e+09}}} & \adjustbox{angle=90}{\shortstack{2.90e+10\\{\scriptsize$\pm$3.08e+09}}} & \adjustbox{angle=90}{\shortstack{2.92e+10\\{\scriptsize$\pm$3.12e+09}}} & \adjustbox{angle=90}{\shortstack{3.03e+10\\{\scriptsize$\pm$2.70e+09}}} & \adjustbox{angle=90}{\shortstack{2.85e+10\\{\scriptsize$\pm$2.94e+09}}} & \adjustbox{angle=90}{\shortstack{2.63e+10\\{\scriptsize$\pm$3.61e+09}}} & \adjustbox{angle=90}{\shortstack{2.87e+10\\{\scriptsize$\pm$2.41e+09}}} & \adjustbox{angle=90}{\shortstack{2.98e+10\\{\scriptsize$\pm$2.97e+09}}} & \adjustbox{angle=90}{\shortstack{2.92e+10\\{\scriptsize$\pm$2.68e+09}}} & \adjustbox{angle=90}{\shortstack{2.62e+10\\{\scriptsize$\pm$3.65e+09}}} & \adjustbox{angle=90}{\shortstack{2.69e+10\\{\scriptsize$\pm$2.77e+09}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.47e+10}\\{\scriptsize$\pm$\textbf{2.97e+09}}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{1.93e+11\\{\scriptsize$\pm$5.69e+09}}} & \adjustbox{angle=90}{\shortstack{1.89e+11\\{\scriptsize$\pm$6.07e+09}}} & \adjustbox{angle=90}{\shortstack{1.97e+11\\{\scriptsize$\pm$6.29e+09}}} & \adjustbox{angle=90}{\shortstack{1.95e+11\\{\scriptsize$\pm$7.06e+09}}} & \adjustbox{angle=90}{\shortstack{1.95e+11\\{\scriptsize$\pm$6.70e+09}}} & \adjustbox{angle=90}{\shortstack{1.96e+11\\{\scriptsize$\pm$7.01e+09}}} & \adjustbox{angle=90}{\shortstack{1.92e+11\\{\scriptsize$\pm$8.03e+09}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.83e+11}\\{\scriptsize$\pm$\textbf{7.60e+09}}}} & \adjustbox{angle=90}{\shortstack{1.96e+11\\{\scriptsize$\pm$5.77e+09}}} & \adjustbox{angle=90}{\shortstack{1.95e+11\\{\scriptsize$\pm$6.26e+09}}} & \adjustbox{angle=90}{\shortstack{1.96e+11\\{\scriptsize$\pm$5.13e+09}}} & \adjustbox{angle=90}{\shortstack{1.89e+11\\{\scriptsize$\pm$7.63e+09}}} & \adjustbox{angle=90}{\shortstack{1.94e+11\\{\scriptsize$\pm$8.53e+09}}} & \adjustbox{angle=90}{\shortstack{1.83e+11\\{\scriptsize$\pm$7.90e+09}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{4.13e+11\\{\scriptsize$\pm$9.65e+09}}} & \adjustbox{angle=90}{\shortstack{4.08e+11\\{\scriptsize$\pm$7.36e+09}}} & \adjustbox{angle=90}{\shortstack{4.17e+11\\{\scriptsize$\pm$8.63e+09}}} & \adjustbox{angle=90}{\shortstack{4.17e+11\\{\scriptsize$\pm$1.02e+10}}} & \adjustbox{angle=90}{\shortstack{4.17e+11\\{\scriptsize$\pm$7.61e+09}}} & \adjustbox{angle=90}{\shortstack{4.19e+11\\{\scriptsize$\pm$9.37e+09}}} & \adjustbox{angle=90}{\shortstack{4.12e+11\\{\scriptsize$\pm$1.08e+10}}} & \adjustbox{angle=90}{\shortstack{3.99e+11\\{\scriptsize$\pm$9.37e+09}}} & \adjustbox{angle=90}{\shortstack{4.16e+11\\{\scriptsize$\pm$1.00e+10}}} & \adjustbox{angle=90}{\shortstack{4.16e+11\\{\scriptsize$\pm$8.84e+09}}} & \adjustbox{angle=90}{\shortstack{4.17e+11\\{\scriptsize$\pm$9.04e+09}}} & \adjustbox{angle=90}{\shortstack{4.09e+11\\{\scriptsize$\pm$9.65e+09}}} & \adjustbox{angle=90}{\shortstack{4.12e+11\\{\scriptsize$\pm$9.16e+09}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{3.97e+11}\\{\scriptsize$\pm$\textbf{1.18e+10}}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:SchwefelN6}}} & 100 & \adjustbox{angle=90}{\shortstack{2.60e+01\\{\scriptsize$\pm$1.51e+01}}} & \adjustbox{angle=90}{\shortstack{5.73e+02\\{\scriptsize$\pm$5.31e+01}}} & \adjustbox{angle=90}{\shortstack{2.32e+01\\{\scriptsize$\pm$4.87e+01}}} & \adjustbox{angle=90}{\shortstack{1.55e+01\\{\scriptsize$\pm$9.81e+00}}} & \adjustbox{angle=90}{\shortstack{1.88e+01\\{\scriptsize$\pm$1.04e+01}}} & \adjustbox{angle=90}{\shortstack{3.36e+01\\{\scriptsize$\pm$4.92e+01}}} & \adjustbox{angle=90}{\shortstack{8.27e+00\\{\scriptsize$\pm$7.25e+00}}} & \adjustbox{angle=90}{\shortstack{2.22e+01\\{\scriptsize$\pm$5.52e+01}}} & \adjustbox{angle=90}{\shortstack{2.20e+01\\{\scriptsize$\pm$1.09e+01}}} & \adjustbox{angle=90}{\shortstack{3.02e+01\\{\scriptsize$\pm$4.60e+01}}} & \adjustbox{angle=90}{\shortstack{1.35e+01\\{\scriptsize$\pm$7.66e+00}}} & \adjustbox{angle=90}{\shortstack{4.21e+00\\{\scriptsize$\pm$2.35e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.09e+00}\\{\scriptsize$\pm$\textbf{8.73e-01}}}} & \adjustbox{angle=90}{\shortstack{8.37e+00\\{\scriptsize$\pm$4.21e+00}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{1.49e+02\\{\scriptsize$\pm$7.07e+01}}} & \adjustbox{angle=90}{\shortstack{3.82e+03\\{\scriptsize$\pm$2.64e+02}}} & \adjustbox{angle=90}{\shortstack{1.05e+02\\{\scriptsize$\pm$1.02e+02}}} & \adjustbox{angle=90}{\shortstack{1.27e+02\\{\scriptsize$\pm$1.03e+02}}} & \adjustbox{angle=90}{\shortstack{1.14e+02\\{\scriptsize$\pm$6.84e+01}}} & \adjustbox{angle=90}{\shortstack{1.48e+02\\{\scriptsize$\pm$1.07e+02}}} & \adjustbox{angle=90}{\shortstack{6.53e+01\\{\scriptsize$\pm$6.25e+01}}} & \adjustbox{angle=90}{\shortstack{8.05e+01\\{\scriptsize$\pm$4.85e+01}}} & \adjustbox{angle=90}{\shortstack{1.17e+02\\{\scriptsize$\pm$6.11e+01}}} & \adjustbox{angle=90}{\shortstack{9.76e+01\\{\scriptsize$\pm$6.53e+01}}} & \adjustbox{angle=90}{\shortstack{9.51e+01\\{\scriptsize$\pm$6.65e+01}}} & \adjustbox{angle=90}{\shortstack{1.86e+01\\{\scriptsize$\pm$1.72e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{5.78e+00}\\{\scriptsize$\pm$\textbf{5.87e+00}}}} & \adjustbox{angle=90}{\shortstack{5.68e+01\\{\scriptsize$\pm$8.43e+01}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{2.33e+02\\{\scriptsize$\pm$1.36e+02}}} & \adjustbox{angle=90}{\shortstack{8.08e+03\\{\scriptsize$\pm$6.65e+02}}} & \adjustbox{angle=90}{\shortstack{2.34e+02\\{\scriptsize$\pm$1.91e+02}}} & \adjustbox{angle=90}{\shortstack{2.49e+02\\{\scriptsize$\pm$2.26e+02}}} & \adjustbox{angle=90}{\shortstack{2.73e+02\\{\scriptsize$\pm$2.08e+02}}} & \adjustbox{angle=90}{\shortstack{3.08e+02\\{\scriptsize$\pm$2.40e+02}}} & \adjustbox{angle=90}{\shortstack{1.74e+02\\{\scriptsize$\pm$2.13e+02}}} & \adjustbox{angle=90}{\shortstack{1.56e+02\\{\scriptsize$\pm$9.45e+01}}} & \adjustbox{angle=90}{\shortstack{2.62e+02\\{\scriptsize$\pm$1.39e+02}}} & \adjustbox{angle=90}{\shortstack{2.00e+02\\{\scriptsize$\pm$1.69e+02}}} & \adjustbox{angle=90}{\shortstack{2.43e+02\\{\scriptsize$\pm$1.63e+02}}} & \adjustbox{angle=90}{\shortstack{4.03e+01\\{\scriptsize$\pm$3.84e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.03e+01}\\{\scriptsize$\pm$\textbf{1.01e+01}}}} & \adjustbox{angle=90}{\shortstack{1.00e+02\\{\scriptsize$\pm$1.04e+02}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:ShiftedSchwefel}}} & 100 & \adjustbox{angle=90}{\shortstack{2.10e+04\\{\scriptsize$\pm$1.91e+03}}} & \adjustbox{angle=90}{\shortstack{1.82e+04\\{\scriptsize$\pm$2.21e+03}}} & \adjustbox{angle=90}{\shortstack{2.11e+04\\{\scriptsize$\pm$4.23e+03}}} & \adjustbox{angle=90}{\shortstack{2.19e+04\\{\scriptsize$\pm$3.13e+03}}} & \adjustbox{angle=90}{\shortstack{2.13e+04\\{\scriptsize$\pm$3.24e+03}}} & \adjustbox{angle=90}{\shortstack{2.32e+04\\{\scriptsize$\pm$2.88e+03}}} & \adjustbox{angle=90}{\shortstack{2.07e+04\\{\scriptsize$\pm$2.81e+03}}} & \adjustbox{angle=90}{\shortstack{1.99e+04\\{\scriptsize$\pm$2.25e+03}}} & \adjustbox{angle=90}{\shortstack{2.04e+04\\{\scriptsize$\pm$3.15e+03}}} & \adjustbox{angle=90}{\shortstack{2.15e+04\\{\scriptsize$\pm$2.95e+03}}} & \adjustbox{angle=90}{\shortstack{2.12e+04\\{\scriptsize$\pm$2.55e+03}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.79e+04}\\{\scriptsize$\pm$\textbf{2.53e+03}}}} & \adjustbox{angle=90}{\shortstack{2.57e+04\\{\scriptsize$\pm$1.75e+03}}} & \adjustbox{angle=90}{\shortstack{2.23e+04\\{\scriptsize$\pm$2.79e+03}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{1.58e+05\\{\scriptsize$\pm$4.25e+03}}} & \adjustbox{angle=90}{\shortstack{1.51e+05\\{\scriptsize$\pm$4.07e+03}}} & \adjustbox{angle=90}{\shortstack{1.56e+05\\{\scriptsize$\pm$7.32e+03}}} & \adjustbox{angle=90}{\shortstack{1.59e+05\\{\scriptsize$\pm$8.80e+03}}} & \adjustbox{angle=90}{\shortstack{1.57e+05\\{\scriptsize$\pm$7.74e+03}}} & \adjustbox{angle=90}{\shortstack{1.63e+05\\{\scriptsize$\pm$6.80e+03}}} & \adjustbox{angle=90}{\shortstack{1.57e+05\\{\scriptsize$\pm$6.98e+03}}} & \adjustbox{angle=90}{\shortstack{1.56e+05\\{\scriptsize$\pm$7.70e+03}}} & \adjustbox{angle=90}{\shortstack{1.57e+05\\{\scriptsize$\pm$6.74e+03}}} & \adjustbox{angle=90}{\shortstack{1.58e+05\\{\scriptsize$\pm$8.14e+03}}} & \adjustbox{angle=90}{\shortstack{1.57e+05\\{\scriptsize$\pm$7.31e+03}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.51e+05}\\{\scriptsize$\pm$\textbf{5.59e+03}}}} & \adjustbox{angle=90}{\shortstack{1.71e+05\\{\scriptsize$\pm$4.66e+03}}} & \adjustbox{angle=90}{\shortstack{1.65e+05\\{\scriptsize$\pm$5.03e+03}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{3.41e+05\\{\scriptsize$\pm$7.53e+03}}} & \adjustbox{angle=90}{\shortstack{3.32e+05\\{\scriptsize$\pm$6.48e+03}}} & \adjustbox{angle=90}{\shortstack{3.41e+05\\{\scriptsize$\pm$1.15e+04}}} & \adjustbox{angle=90}{\shortstack{3.41e+05\\{\scriptsize$\pm$1.12e+04}}} & \adjustbox{angle=90}{\shortstack{3.38e+05\\{\scriptsize$\pm$1.18e+04}}} & \adjustbox{angle=90}{\shortstack{3.48e+05\\{\scriptsize$\pm$9.66e+03}}} & \adjustbox{angle=90}{\shortstack{3.38e+05\\{\scriptsize$\pm$1.09e+04}}} & \adjustbox{angle=90}{\shortstack{3.36e+05\\{\scriptsize$\pm$9.52e+03}}} & \adjustbox{angle=90}{\shortstack{3.40e+05\\{\scriptsize$\pm$9.56e+03}}} & \adjustbox{angle=90}{\shortstack{3.42e+05\\{\scriptsize$\pm$1.22e+04}}} & \adjustbox{angle=90}{\shortstack{3.43e+05\\{\scriptsize$\pm$9.75e+03}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{3.27e+05}\\{\scriptsize$\pm$\textbf{9.15e+03}}}} & \adjustbox{angle=90}{\shortstack{3.59e+05\\{\scriptsize$\pm$6.04e+03}}} & \adjustbox{angle=90}{\shortstack{3.49e+05\\{\scriptsize$\pm$7.09e+03}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:ShiftedRotatedHGBat}}} & 100 & \adjustbox{angle=90}{\shortstack{1.64e+02\\{\scriptsize$\pm$2.52e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{7.49e+01}\\{\scriptsize$\pm$\textbf{1.59e+01}}}} & \adjustbox{angle=90}{\shortstack{1.06e+02\\{\scriptsize$\pm$1.61e+01}}} & \adjustbox{angle=90}{\shortstack{1.26e+02\\{\scriptsize$\pm$2.40e+01}}} & \adjustbox{angle=90}{\shortstack{1.13e+02\\{\scriptsize$\pm$1.84e+01}}} & \adjustbox{angle=90}{\shortstack{2.05e+02\\{\scriptsize$\pm$4.25e+01}}} & \adjustbox{angle=90}{\shortstack{1.42e+02\\{\scriptsize$\pm$2.73e+01}}} & \adjustbox{angle=90}{\shortstack{1.25e+02\\{\scriptsize$\pm$2.35e+01}}} & \adjustbox{angle=90}{\shortstack{1.38e+02\\{\scriptsize$\pm$2.16e+01}}} & \adjustbox{angle=90}{\shortstack{1.60e+02\\{\scriptsize$\pm$3.30e+01}}} & \adjustbox{angle=90}{\shortstack{1.54e+02\\{\scriptsize$\pm$2.76e+01}}} & \adjustbox{angle=90}{\shortstack{5.02e+02\\{\scriptsize$\pm$5.53e+01}}} & \adjustbox{angle=90}{\shortstack{6.20e+02\\{\scriptsize$\pm$4.87e+01}}} & \adjustbox{angle=90}{\shortstack{5.74e+02\\{\scriptsize$\pm$5.75e+01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{3.25e+03\\{\scriptsize$\pm$1.03e+02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.31e+03}\\{\scriptsize$\pm$\textbf{8.20e+01}}}} & \adjustbox{angle=90}{\shortstack{3.07e+03\\{\scriptsize$\pm$1.13e+02}}} & \adjustbox{angle=90}{\shortstack{3.11e+03\\{\scriptsize$\pm$9.35e+01}}} & \adjustbox{angle=90}{\shortstack{3.11e+03\\{\scriptsize$\pm$1.01e+02}}} & \adjustbox{angle=90}{\shortstack{3.39e+03\\{\scriptsize$\pm$8.34e+01}}} & \adjustbox{angle=90}{\shortstack{3.20e+03\\{\scriptsize$\pm$8.57e+01}}} & \adjustbox{angle=90}{\shortstack{3.12e+03\\{\scriptsize$\pm$8.48e+01}}} & \adjustbox{angle=90}{\shortstack{3.16e+03\\{\scriptsize$\pm$8.91e+01}}} & \adjustbox{angle=90}{\shortstack{3.27e+03\\{\scriptsize$\pm$9.01e+01}}} & \adjustbox{angle=90}{\shortstack{3.23e+03\\{\scriptsize$\pm$9.82e+01}}} & \adjustbox{angle=90}{\shortstack{3.71e+03\\{\scriptsize$\pm$5.94e+01}}} & \adjustbox{angle=90}{\shortstack{3.81e+03\\{\scriptsize$\pm$4.98e+01}}} & \adjustbox{angle=90}{\shortstack{3.77e+03\\{\scriptsize$\pm$5.93e+01}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{7.74e+03\\{\scriptsize$\pm$9.38e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{6.26e+03}\\{\scriptsize$\pm$\textbf{1.28e+02}}}} & \adjustbox{angle=90}{\shortstack{7.49e+03\\{\scriptsize$\pm$1.16e+02}}} & \adjustbox{angle=90}{\shortstack{7.55e+03\\{\scriptsize$\pm$1.12e+02}}} & \adjustbox{angle=90}{\shortstack{7.59e+03\\{\scriptsize$\pm$1.17e+02}}} & \adjustbox{angle=90}{\shortstack{7.83e+03\\{\scriptsize$\pm$1.06e+02}}} & \adjustbox{angle=90}{\shortstack{7.63e+03\\{\scriptsize$\pm$8.74e+01}}} & \adjustbox{angle=90}{\shortstack{7.56e+03\\{\scriptsize$\pm$9.92e+01}}} & \adjustbox{angle=90}{\shortstack{7.63e+03\\{\scriptsize$\pm$1.20e+02}}} & \adjustbox{angle=90}{\shortstack{7.71e+03\\{\scriptsize$\pm$1.14e+02}}} & \adjustbox{angle=90}{\shortstack{7.65e+03\\{\scriptsize$\pm$1.01e+02}}} & \adjustbox{angle=90}{\shortstack{8.16e+03\\{\scriptsize$\pm$6.19e+01}}} & \adjustbox{angle=90}{\shortstack{8.23e+03\\{\scriptsize$\pm$5.96e+01}}} & \adjustbox{angle=90}{\shortstack{8.20e+03\\{\scriptsize$\pm$5.58e+01}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:ShiftedRotatedHappyCat}}} & 100 & \adjustbox{angle=90}{\shortstack{4.10e+00\\{\scriptsize$\pm$3.92e-01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.37e+00}\\{\scriptsize$\pm$\textbf{8.20e-01}}}} & \adjustbox{angle=90}{\shortstack{2.70e+00\\{\scriptsize$\pm$1.03e+00}}} & \adjustbox{angle=90}{\shortstack{3.53e+00\\{\scriptsize$\pm$5.28e-01}}} & \adjustbox{angle=90}{\shortstack{3.35e+00\\{\scriptsize$\pm$6.18e-01}}} & \adjustbox{angle=90}{\shortstack{4.65e+00\\{\scriptsize$\pm$4.48e-01}}} & \adjustbox{angle=90}{\shortstack{3.83e+00\\{\scriptsize$\pm$6.13e-01}}} & \adjustbox{angle=90}{\shortstack{3.35e+00\\{\scriptsize$\pm$7.63e-01}}} & \adjustbox{angle=90}{\shortstack{3.61e+00\\{\scriptsize$\pm$5.20e-01}}} & \adjustbox{angle=90}{\shortstack{4.21e+00\\{\scriptsize$\pm$4.36e-01}}} & \adjustbox{angle=90}{\shortstack{3.81e+00\\{\scriptsize$\pm$4.91e-01}}} & \adjustbox{angle=90}{\shortstack{7.53e+00\\{\scriptsize$\pm$4.81e-01}}} & \adjustbox{angle=90}{\shortstack{8.53e+00\\{\scriptsize$\pm$4.40e-01}}} & \adjustbox{angle=90}{\shortstack{8.03e+00\\{\scriptsize$\pm$4.80e-01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{1.09e+01\\{\scriptsize$\pm$1.52e-01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{9.20e+00}\\{\scriptsize$\pm$\textbf{1.46e-01}}}} & \adjustbox{angle=90}{\shortstack{1.05e+01\\{\scriptsize$\pm$1.93e-01}}} & \adjustbox{angle=90}{\shortstack{1.06e+01\\{\scriptsize$\pm$1.74e-01}}} & \adjustbox{angle=90}{\shortstack{1.07e+01\\{\scriptsize$\pm$1.52e-01}}} & \adjustbox{angle=90}{\shortstack{1.11e+01\\{\scriptsize$\pm$1.81e-01}}} & \adjustbox{angle=90}{\shortstack{1.08e+01\\{\scriptsize$\pm$1.60e-01}}} & \adjustbox{angle=90}{\shortstack{1.07e+01\\{\scriptsize$\pm$1.98e-01}}} & \adjustbox{angle=90}{\shortstack{1.08e+01\\{\scriptsize$\pm$2.20e-01}}} & \adjustbox{angle=90}{\shortstack{1.09e+01\\{\scriptsize$\pm$1.40e-01}}} & \adjustbox{angle=90}{\shortstack{1.08e+01\\{\scriptsize$\pm$1.49e-01}}} & \adjustbox{angle=90}{\shortstack{1.17e+01\\{\scriptsize$\pm$9.74e-02}}} & \adjustbox{angle=90}{\shortstack{1.18e+01\\{\scriptsize$\pm$9.75e-02}}} & \adjustbox{angle=90}{\shortstack{1.18e+01\\{\scriptsize$\pm$8.92e-02}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{1.35e+01\\{\scriptsize$\pm$8.90e-02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.21e+01}\\{\scriptsize$\pm$\textbf{1.15e-01}}}} & \adjustbox{angle=90}{\shortstack{1.32e+01\\{\scriptsize$\pm$9.14e-02}}} & \adjustbox{angle=90}{\shortstack{1.33e+01\\{\scriptsize$\pm$9.66e-02}}} & \adjustbox{angle=90}{\shortstack{1.33e+01\\{\scriptsize$\pm$8.31e-02}}} & \adjustbox{angle=90}{\shortstack{1.35e+01\\{\scriptsize$\pm$8.48e-02}}} & \adjustbox{angle=90}{\shortstack{1.33e+01\\{\scriptsize$\pm$9.20e-02}}} & \adjustbox{angle=90}{\shortstack{1.33e+01\\{\scriptsize$\pm$9.95e-02}}} & \adjustbox{angle=90}{\shortstack{1.34e+01\\{\scriptsize$\pm$9.26e-02}}} & \adjustbox{angle=90}{\shortstack{1.34e+01\\{\scriptsize$\pm$8.42e-02}}} & \adjustbox{angle=90}{\shortstack{1.34e+01\\{\scriptsize$\pm$7.36e-02}}} & \adjustbox{angle=90}{\shortstack{1.38e+01\\{\scriptsize$\pm$5.69e-02}}} & \adjustbox{angle=90}{\shortstack{1.39e+01\\{\scriptsize$\pm$6.01e-02}}} & \adjustbox{angle=90}{\shortstack{1.38e+01\\{\scriptsize$\pm$6.66e-02}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:ShiftedRotatedSchafferF7}}} & 100 & \adjustbox{angle=90}{\shortstack{5.24e+11\\{\scriptsize$\pm$9.77e+10}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{3.36e+11}\\{\scriptsize$\pm$\textbf{5.42e+10}}}} & \adjustbox{angle=90}{\shortstack{5.25e+11\\{\scriptsize$\pm$1.04e+11}}} & \adjustbox{angle=90}{\shortstack{4.87e+11\\{\scriptsize$\pm$1.11e+11}}} & \adjustbox{angle=90}{\shortstack{4.11e+11\\{\scriptsize$\pm$1.14e+11}}} & \adjustbox{angle=90}{\shortstack{5.53e+11\\{\scriptsize$\pm$9.25e+10}}} & \adjustbox{angle=90}{\shortstack{5.23e+11\\{\scriptsize$\pm$9.02e+10}}} & \adjustbox{angle=90}{\shortstack{4.55e+11\\{\scriptsize$\pm$1.03e+11}}} & \adjustbox{angle=90}{\shortstack{4.32e+11\\{\scriptsize$\pm$1.09e+11}}} & \adjustbox{angle=90}{\shortstack{5.23e+11\\{\scriptsize$\pm$1.19e+11}}} & \adjustbox{angle=90}{\shortstack{4.75e+11\\{\scriptsize$\pm$1.32e+11}}} & \adjustbox{angle=90}{\shortstack{5.37e+11\\{\scriptsize$\pm$6.81e+10}}} & \adjustbox{angle=90}{\shortstack{5.86e+11\\{\scriptsize$\pm$7.50e+10}}} & \adjustbox{angle=90}{\shortstack{5.67e+11\\{\scriptsize$\pm$6.18e+10}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{9.23e+11\\{\scriptsize$\pm$2.98e+10}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{6.43e+11}\\{\scriptsize$\pm$\textbf{3.08e+10}}}} & \adjustbox{angle=90}{\shortstack{9.09e+11\\{\scriptsize$\pm$2.90e+10}}} & \adjustbox{angle=90}{\shortstack{8.97e+11\\{\scriptsize$\pm$3.41e+10}}} & \adjustbox{angle=90}{\shortstack{8.99e+11\\{\scriptsize$\pm$3.63e+10}}} & \adjustbox{angle=90}{\shortstack{9.24e+11\\{\scriptsize$\pm$2.83e+10}}} & \adjustbox{angle=90}{\shortstack{8.96e+11\\{\scriptsize$\pm$3.61e+10}}} & \adjustbox{angle=90}{\shortstack{9.05e+11\\{\scriptsize$\pm$2.71e+10}}} & \adjustbox{angle=90}{\shortstack{9.06e+11\\{\scriptsize$\pm$3.71e+10}}} & \adjustbox{angle=90}{\shortstack{9.39e+11\\{\scriptsize$\pm$2.60e+10}}} & \adjustbox{angle=90}{\shortstack{9.14e+11\\{\scriptsize$\pm$3.23e+10}}} & \adjustbox{angle=90}{\shortstack{9.05e+11\\{\scriptsize$\pm$2.44e+10}}} & \adjustbox{angle=90}{\shortstack{9.36e+11\\{\scriptsize$\pm$2.56e+10}}} & \adjustbox{angle=90}{\shortstack{9.34e+11\\{\scriptsize$\pm$2.77e+10}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{9.40e+11\\{\scriptsize$\pm$1.67e+10}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{7.03e+11}\\{\scriptsize$\pm$\textbf{2.36e+10}}}} & \adjustbox{angle=90}{\shortstack{9.16e+11\\{\scriptsize$\pm$2.44e+10}}} & \adjustbox{angle=90}{\shortstack{9.17e+11\\{\scriptsize$\pm$2.42e+10}}} & \adjustbox{angle=90}{\shortstack{9.15e+11\\{\scriptsize$\pm$2.35e+10}}} & \adjustbox{angle=90}{\shortstack{9.37e+11\\{\scriptsize$\pm$2.18e+10}}} & \adjustbox{angle=90}{\shortstack{9.17e+11\\{\scriptsize$\pm$1.73e+10}}} & \adjustbox{angle=90}{\shortstack{9.12e+11\\{\scriptsize$\pm$1.91e+10}}} & \adjustbox{angle=90}{\shortstack{9.31e+11\\{\scriptsize$\pm$2.06e+10}}} & \adjustbox{angle=90}{\shortstack{9.40e+11\\{\scriptsize$\pm$1.62e+10}}} & \adjustbox{angle=90}{\shortstack{9.28e+11\\{\scriptsize$\pm$1.84e+10}}} & \adjustbox{angle=90}{\shortstack{9.22e+11\\{\scriptsize$\pm$1.63e+10}}} & \adjustbox{angle=90}{\shortstack{9.41e+11\\{\scriptsize$\pm$1.12e+10}}} & \adjustbox{angle=90}{\shortstack{9.52e+11\\{\scriptsize$\pm$1.68e+10}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:ShiftedRotatedWeierstrass}}} & 100 & \adjustbox{angle=90}{\shortstack{1.51e+02\\{\scriptsize$\pm$5.83e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.22e+02}\\{\scriptsize$\pm$\textbf{6.59e+00}}}} & \adjustbox{angle=90}{\shortstack{1.51e+02\\{\scriptsize$\pm$6.67e+00}}} & \adjustbox{angle=90}{\shortstack{1.49e+02\\{\scriptsize$\pm$7.74e+00}}} & \adjustbox{angle=90}{\shortstack{1.48e+02\\{\scriptsize$\pm$6.44e+00}}} & \adjustbox{angle=90}{\shortstack{1.53e+02\\{\scriptsize$\pm$4.92e+00}}} & \adjustbox{angle=90}{\shortstack{1.50e+02\\{\scriptsize$\pm$5.15e+00}}} & \adjustbox{angle=90}{\shortstack{1.48e+02\\{\scriptsize$\pm$6.91e+00}}} & \adjustbox{angle=90}{\shortstack{1.48e+02\\{\scriptsize$\pm$5.95e+00}}} & \adjustbox{angle=90}{\shortstack{1.50e+02\\{\scriptsize$\pm$6.61e+00}}} & \adjustbox{angle=90}{\shortstack{1.48e+02\\{\scriptsize$\pm$6.12e+00}}} & \adjustbox{angle=90}{\shortstack{1.53e+02\\{\scriptsize$\pm$5.66e+00}}} & \adjustbox{angle=90}{\shortstack{1.58e+02\\{\scriptsize$\pm$5.29e+00}}} & \adjustbox{angle=90}{\shortstack{1.54e+02\\{\scriptsize$\pm$6.25e+00}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{8.78e+02\\{\scriptsize$\pm$1.19e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{7.99e+02}\\{\scriptsize$\pm$\textbf{1.84e+01}}}} & \adjustbox{angle=90}{\shortstack{8.71e+02\\{\scriptsize$\pm$1.54e+01}}} & \adjustbox{angle=90}{\shortstack{8.71e+02\\{\scriptsize$\pm$1.39e+01}}} & \adjustbox{angle=90}{\shortstack{8.69e+02\\{\scriptsize$\pm$1.42e+01}}} & \adjustbox{angle=90}{\shortstack{8.79e+02\\{\scriptsize$\pm$1.45e+01}}} & \adjustbox{angle=90}{\shortstack{8.69e+02\\{\scriptsize$\pm$1.36e+01}}} & \adjustbox{angle=90}{\shortstack{8.67e+02\\{\scriptsize$\pm$1.21e+01}}} & \adjustbox{angle=90}{\shortstack{8.69e+02\\{\scriptsize$\pm$1.50e+01}}} & \adjustbox{angle=90}{\shortstack{8.71e+02\\{\scriptsize$\pm$1.46e+01}}} & \adjustbox{angle=90}{\shortstack{8.72e+02\\{\scriptsize$\pm$1.32e+01}}} & \adjustbox{angle=90}{\shortstack{8.78e+02\\{\scriptsize$\pm$1.46e+01}}} & \adjustbox{angle=90}{\shortstack{8.80e+02\\{\scriptsize$\pm$1.16e+01}}} & \adjustbox{angle=90}{\shortstack{8.83e+02\\{\scriptsize$\pm$1.57e+01}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{1.75e+03\\{\scriptsize$\pm$1.37e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.69e+03}\\{\scriptsize$\pm$\textbf{2.79e+01}}}} & \adjustbox{angle=90}{\shortstack{1.77e+03\\{\scriptsize$\pm$2.66e+01}}} & \adjustbox{angle=90}{\shortstack{1.76e+03\\{\scriptsize$\pm$2.43e+01}}} & \adjustbox{angle=90}{\shortstack{1.76e+03\\{\scriptsize$\pm$2.58e+01}}} & \adjustbox{angle=90}{\shortstack{1.76e+03\\{\scriptsize$\pm$2.37e+01}}} & \adjustbox{angle=90}{\shortstack{1.75e+03\\{\scriptsize$\pm$1.93e+01}}} & \adjustbox{angle=90}{\shortstack{1.75e+03\\{\scriptsize$\pm$2.04e+01}}} & \adjustbox{angle=90}{\shortstack{1.76e+03\\{\scriptsize$\pm$2.27e+01}}} & \adjustbox{angle=90}{\shortstack{1.75e+03\\{\scriptsize$\pm$2.62e+01}}} & \adjustbox{angle=90}{\shortstack{1.75e+03\\{\scriptsize$\pm$2.39e+01}}} & \adjustbox{angle=90}{\shortstack{1.75e+03\\{\scriptsize$\pm$1.50e+01}}} & \adjustbox{angle=90}{\shortstack{1.75e+03\\{\scriptsize$\pm$1.13e+01}}} & \adjustbox{angle=90}{\shortstack{1.75e+03\\{\scriptsize$\pm$1.32e+01}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:ShubertN3}}} & 100 & \adjustbox{angle=90}{\shortstack{1.21e+03\\{\scriptsize$\pm$4.50e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{8.51e+02}\\{\scriptsize$\pm$\textbf{4.17e+01}}}} & \adjustbox{angle=90}{\shortstack{1.13e+03\\{\scriptsize$\pm$5.96e+01}}} & \adjustbox{angle=90}{\shortstack{1.13e+03\\{\scriptsize$\pm$6.32e+01}}} & \adjustbox{angle=90}{\shortstack{1.13e+03\\{\scriptsize$\pm$5.42e+01}}} & \adjustbox{angle=90}{\shortstack{1.16e+03\\{\scriptsize$\pm$5.43e+01}}} & \adjustbox{angle=90}{\shortstack{1.12e+03\\{\scriptsize$\pm$5.26e+01}}} & \adjustbox{angle=90}{\shortstack{1.12e+03\\{\scriptsize$\pm$4.53e+01}}} & \adjustbox{angle=90}{\shortstack{1.15e+03\\{\scriptsize$\pm$4.73e+01}}} & \adjustbox{angle=90}{\shortstack{1.16e+03\\{\scriptsize$\pm$4.29e+01}}} & \adjustbox{angle=90}{\shortstack{1.15e+03\\{\scriptsize$\pm$5.06e+01}}} & \adjustbox{angle=90}{\shortstack{1.07e+03\\{\scriptsize$\pm$3.85e+01}}} & \adjustbox{angle=90}{\shortstack{1.16e+03\\{\scriptsize$\pm$3.44e+01}}} & \adjustbox{angle=90}{\shortstack{1.13e+03\\{\scriptsize$\pm$6.06e+01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{6.83e+03\\{\scriptsize$\pm$8.87e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{5.04e+03}\\{\scriptsize$\pm$\textbf{1.31e+02}}}} & \adjustbox{angle=90}{\shortstack{6.61e+03\\{\scriptsize$\pm$1.21e+02}}} & \adjustbox{angle=90}{\shortstack{6.64e+03\\{\scriptsize$\pm$1.11e+02}}} & \adjustbox{angle=90}{\shortstack{6.61e+03\\{\scriptsize$\pm$1.22e+02}}} & \adjustbox{angle=90}{\shortstack{6.72e+03\\{\scriptsize$\pm$1.11e+02}}} & \adjustbox{angle=90}{\shortstack{6.59e+03\\{\scriptsize$\pm$9.20e+01}}} & \adjustbox{angle=90}{\shortstack{6.62e+03\\{\scriptsize$\pm$9.61e+01}}} & \adjustbox{angle=90}{\shortstack{6.68e+03\\{\scriptsize$\pm$1.18e+02}}} & \adjustbox{angle=90}{\shortstack{6.66e+03\\{\scriptsize$\pm$1.41e+02}}} & \adjustbox{angle=90}{\shortstack{6.67e+03\\{\scriptsize$\pm$1.15e+02}}} & \adjustbox{angle=90}{\shortstack{6.47e+03\\{\scriptsize$\pm$8.97e+01}}} & \adjustbox{angle=90}{\shortstack{6.72e+03\\{\scriptsize$\pm$7.78e+01}}} & \adjustbox{angle=90}{\shortstack{6.67e+03\\{\scriptsize$\pm$1.35e+02}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{1.40e+04\\{\scriptsize$\pm$1.49e+02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.11e+04}\\{\scriptsize$\pm$\textbf{2.32e+02}}}} & \adjustbox{angle=90}{\shortstack{1.37e+04\\{\scriptsize$\pm$2.05e+02}}} & \adjustbox{angle=90}{\shortstack{1.37e+04\\{\scriptsize$\pm$1.53e+02}}} & \adjustbox{angle=90}{\shortstack{1.38e+04\\{\scriptsize$\pm$1.65e+02}}} & \adjustbox{angle=90}{\shortstack{1.38e+04\\{\scriptsize$\pm$1.94e+02}}} & \adjustbox{angle=90}{\shortstack{1.37e+04\\{\scriptsize$\pm$1.69e+02}}} & \adjustbox{angle=90}{\shortstack{1.37e+04\\{\scriptsize$\pm$1.55e+02}}} & \adjustbox{angle=90}{\shortstack{1.38e+04\\{\scriptsize$\pm$1.46e+02}}} & \adjustbox{angle=90}{\shortstack{1.38e+04\\{\scriptsize$\pm$1.85e+02}}} & \adjustbox{angle=90}{\shortstack{1.39e+04\\{\scriptsize$\pm$1.49e+02}}} & \adjustbox{angle=90}{\shortstack{1.35e+04\\{\scriptsize$\pm$1.24e+02}}} & \adjustbox{angle=90}{\shortstack{1.39e+04\\{\scriptsize$\pm$1.37e+02}}} & \adjustbox{angle=90}{\shortstack{1.38e+04\\{\scriptsize$\pm$1.53e+02}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:ShubertN4}}} & 100 & \adjustbox{angle=90}{\shortstack{8.66e+02\\{\scriptsize$\pm$1.61e+02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{6.08e+02}\\{\scriptsize$\pm$\textbf{1.14e+02}}}} & \adjustbox{angle=90}{\shortstack{1.14e+03\\{\scriptsize$\pm$1.53e+02}}} & \adjustbox{angle=90}{\shortstack{1.17e+03\\{\scriptsize$\pm$7.79e+01}}} & \adjustbox{angle=90}{\shortstack{1.05e+03\\{\scriptsize$\pm$2.11e+02}}} & \adjustbox{angle=90}{\shortstack{9.76e+02\\{\scriptsize$\pm$1.61e+02}}} & \adjustbox{angle=90}{\shortstack{1.18e+03\\{\scriptsize$\pm$5.01e+01}}} & \adjustbox{angle=90}{\shortstack{9.68e+02\\{\scriptsize$\pm$1.89e+02}}} & \adjustbox{angle=90}{\shortstack{1.05e+03\\{\scriptsize$\pm$1.76e+02}}} & \adjustbox{angle=90}{\shortstack{1.13e+03\\{\scriptsize$\pm$9.85e+01}}} & \adjustbox{angle=90}{\shortstack{1.09e+03\\{\scriptsize$\pm$1.44e+02}}} & \adjustbox{angle=90}{\shortstack{8.28e+02\\{\scriptsize$\pm$1.32e+02}}} & \adjustbox{angle=90}{\shortstack{6.10e+02\\{\scriptsize$\pm$2.23e+02}}} & \adjustbox{angle=90}{\shortstack{7.99e+02\\{\scriptsize$\pm$1.46e+02}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{5.56e+03\\{\scriptsize$\pm$8.95e+02}}} & \adjustbox{angle=90}{\shortstack{3.05e+03\\{\scriptsize$\pm$3.80e+02}}} & \adjustbox{angle=90}{\shortstack{5.36e+03\\{\scriptsize$\pm$1.30e+03}}} & \adjustbox{angle=90}{\shortstack{6.30e+03\\{\scriptsize$\pm$1.55e+02}}} & \adjustbox{angle=90}{\shortstack{5.44e+03\\{\scriptsize$\pm$1.20e+03}}} & \adjustbox{angle=90}{\shortstack{5.21e+03\\{\scriptsize$\pm$9.16e+02}}} & \adjustbox{angle=90}{\shortstack{6.16e+03\\{\scriptsize$\pm$1.51e+02}}} & \adjustbox{angle=90}{\shortstack{5.09e+03\\{\scriptsize$\pm$8.61e+02}}} & \adjustbox{angle=90}{\shortstack{5.44e+03\\{\scriptsize$\pm$1.09e+03}}} & \adjustbox{angle=90}{\shortstack{6.21e+03\\{\scriptsize$\pm$2.31e+02}}} & \adjustbox{angle=90}{\shortstack{5.46e+03\\{\scriptsize$\pm$9.26e+02}}} & \adjustbox{angle=90}{\shortstack{4.03e+03\\{\scriptsize$\pm$7.40e+02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.89e+03}\\{\scriptsize$\pm$\textbf{8.37e+02}}}} & \adjustbox{angle=90}{\shortstack{4.06e+03\\{\scriptsize$\pm$1.09e+03}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{1.15e+04\\{\scriptsize$\pm$1.63e+03}}} & \adjustbox{angle=90}{\shortstack{6.29e+03\\{\scriptsize$\pm$7.43e+02}}} & \adjustbox{angle=90}{\shortstack{1.11e+04\\{\scriptsize$\pm$2.60e+03}}} & \adjustbox{angle=90}{\shortstack{1.26e+04\\{\scriptsize$\pm$5.48e+02}}} & \adjustbox{angle=90}{\shortstack{1.06e+04\\{\scriptsize$\pm$2.70e+03}}} & \adjustbox{angle=90}{\shortstack{1.02e+04\\{\scriptsize$\pm$2.10e+03}}} & \adjustbox{angle=90}{\shortstack{1.24e+04\\{\scriptsize$\pm$1.93e+02}}} & \adjustbox{angle=90}{\shortstack{1.02e+04\\{\scriptsize$\pm$1.71e+03}}} & \adjustbox{angle=90}{\shortstack{1.16e+04\\{\scriptsize$\pm$1.99e+03}}} & \adjustbox{angle=90}{\shortstack{1.26e+04\\{\scriptsize$\pm$2.71e+02}}} & \adjustbox{angle=90}{\shortstack{1.11e+04\\{\scriptsize$\pm$1.82e+03}}} & \adjustbox{angle=90}{\shortstack{8.04e+03\\{\scriptsize$\pm$1.38e+03}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{5.98e+03}\\{\scriptsize$\pm$\textbf{1.84e+03}}}} & \adjustbox{angle=90}{\shortstack{8.13e+03\\{\scriptsize$\pm$1.90e+03}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:SineEnvelope}}} & 100 & \adjustbox{angle=90}{\shortstack{6.32e+01\\{\scriptsize$\pm$4.02e+00}}} & \adjustbox{angle=90}{\shortstack{5.44e+01\\{\scriptsize$\pm$3.12e+00}}} & \adjustbox{angle=90}{\shortstack{6.32e+01\\{\scriptsize$\pm$3.14e+00}}} & \adjustbox{angle=90}{\shortstack{6.31e+01\\{\scriptsize$\pm$3.55e+00}}} & \adjustbox{angle=90}{\shortstack{6.11e+01\\{\scriptsize$\pm$3.15e+00}}} & \adjustbox{angle=90}{\shortstack{5.95e+01\\{\scriptsize$\pm$3.66e+00}}} & \adjustbox{angle=90}{\shortstack{5.83e+01\\{\scriptsize$\pm$4.22e+00}}} & \adjustbox{angle=90}{\shortstack{5.82e+01\\{\scriptsize$\pm$3.00e+00}}} & \adjustbox{angle=90}{\shortstack{6.20e+01\\{\scriptsize$\pm$3.25e+00}}} & \adjustbox{angle=90}{\shortstack{6.23e+01\\{\scriptsize$\pm$3.85e+00}}} & \adjustbox{angle=90}{\shortstack{6.16e+01\\{\scriptsize$\pm$2.93e+00}}} & \adjustbox{angle=90}{\shortstack{5.16e+01\\{\scriptsize$\pm$3.38e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{4.96e+01}\\{\scriptsize$\pm$\textbf{2.31e-01}}}} & \adjustbox{angle=90}{\shortstack{5.00e+01\\{\scriptsize$\pm$8.92e-01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{3.25e+02\\{\scriptsize$\pm$1.84e+01}}} & \adjustbox{angle=90}{\shortstack{2.89e+02\\{\scriptsize$\pm$1.54e+01}}} & \adjustbox{angle=90}{\shortstack{3.48e+02\\{\scriptsize$\pm$1.15e+01}}} & \adjustbox{angle=90}{\shortstack{3.37e+02\\{\scriptsize$\pm$1.73e+01}}} & \adjustbox{angle=90}{\shortstack{3.32e+02\\{\scriptsize$\pm$1.59e+01}}} & \adjustbox{angle=90}{\shortstack{3.17e+02\\{\scriptsize$\pm$2.36e+01}}} & \adjustbox{angle=90}{\shortstack{2.95e+02\\{\scriptsize$\pm$9.33e+00}}} & \adjustbox{angle=90}{\shortstack{2.93e+02\\{\scriptsize$\pm$2.11e+01}}} & \adjustbox{angle=90}{\shortstack{3.27e+02\\{\scriptsize$\pm$1.85e+01}}} & \adjustbox{angle=90}{\shortstack{3.20e+02\\{\scriptsize$\pm$2.04e+01}}} & \adjustbox{angle=90}{\shortstack{3.32e+02\\{\scriptsize$\pm$1.69e+01}}} & \adjustbox{angle=90}{\shortstack{2.53e+02\\{\scriptsize$\pm$5.89e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.50e+02}\\{\scriptsize$\pm$\textbf{8.90e-01}}}} & \adjustbox{angle=90}{\shortstack{2.54e+02\\{\scriptsize$\pm$5.95e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{6.43e+02\\{\scriptsize$\pm$3.87e+01}}} & \adjustbox{angle=90}{\shortstack{5.95e+02\\{\scriptsize$\pm$2.73e+01}}} & \adjustbox{angle=90}{\shortstack{6.98e+02\\{\scriptsize$\pm$2.75e+01}}} & \adjustbox{angle=90}{\shortstack{6.85e+02\\{\scriptsize$\pm$2.79e+01}}} & \adjustbox{angle=90}{\shortstack{6.80e+02\\{\scriptsize$\pm$3.29e+01}}} & \adjustbox{angle=90}{\shortstack{6.48e+02\\{\scriptsize$\pm$4.47e+01}}} & \adjustbox{angle=90}{\shortstack{5.89e+02\\{\scriptsize$\pm$1.95e+01}}} & \adjustbox{angle=90}{\shortstack{5.72e+02\\{\scriptsize$\pm$3.22e+01}}} & \adjustbox{angle=90}{\shortstack{6.69e+02\\{\scriptsize$\pm$4.20e+01}}} & \adjustbox{angle=90}{\shortstack{6.45e+02\\{\scriptsize$\pm$3.55e+01}}} & \adjustbox{angle=90}{\shortstack{6.65e+02\\{\scriptsize$\pm$2.88e+01}}} & \adjustbox{angle=90}{\shortstack{5.14e+02\\{\scriptsize$\pm$2.24e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{5.01e+02}\\{\scriptsize$\pm$\textbf{3.13e+00}}}} & \adjustbox{angle=90}{\shortstack{5.09e+02\\{\scriptsize$\pm$9.01e+00}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:Stochastic}}} & 100 & \adjustbox{angle=90}{\shortstack{1.03e+00\\{\scriptsize$\pm$5.46e-01}}} & \adjustbox{angle=90}{\shortstack{2.32e+01\\{\scriptsize$\pm$2.91e+00}}} & \adjustbox{angle=90}{\shortstack{7.17e-01\\{\scriptsize$\pm$5.73e-01}}} & \adjustbox{angle=90}{\shortstack{7.27e-01\\{\scriptsize$\pm$4.90e-01}}} & \adjustbox{angle=90}{\shortstack{7.92e-01\\{\scriptsize$\pm$4.29e-01}}} & \adjustbox{angle=90}{\shortstack{1.00e+00\\{\scriptsize$\pm$8.31e-01}}} & \adjustbox{angle=90}{\shortstack{5.84e-01\\{\scriptsize$\pm$2.76e-01}}} & \adjustbox{angle=90}{\shortstack{5.71e-01\\{\scriptsize$\pm$2.04e-01}}} & \adjustbox{angle=90}{\shortstack{8.16e-01\\{\scriptsize$\pm$4.73e-01}}} & \adjustbox{angle=90}{\shortstack{6.86e-01\\{\scriptsize$\pm$2.89e-01}}} & \adjustbox{angle=90}{\shortstack{7.89e-01\\{\scriptsize$\pm$4.35e-01}}} & \adjustbox{angle=90}{\shortstack{5.24e-01\\{\scriptsize$\pm$2.85e-01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{4.13e-01}\\{\scriptsize$\pm$\textbf{3.32e-02}}}} & \adjustbox{angle=90}{\shortstack{5.04e-01\\{\scriptsize$\pm$1.10e-01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{3.31e+00\\{\scriptsize$\pm$2.42e+00}}} & \adjustbox{angle=90}{\shortstack{1.30e+02\\{\scriptsize$\pm$1.26e+01}}} & \adjustbox{angle=90}{\shortstack{4.22e+00\\{\scriptsize$\pm$5.97e+00}}} & \adjustbox{angle=90}{\shortstack{3.06e+00\\{\scriptsize$\pm$2.27e+00}}} & \adjustbox{angle=90}{\shortstack{2.89e+00\\{\scriptsize$\pm$1.70e+00}}} & \adjustbox{angle=90}{\shortstack{3.80e+00\\{\scriptsize$\pm$3.93e+00}}} & \adjustbox{angle=90}{\shortstack{1.73e+00\\{\scriptsize$\pm$1.52e+00}}} & \adjustbox{angle=90}{\shortstack{2.72e+00\\{\scriptsize$\pm$1.96e+00}}} & \adjustbox{angle=90}{\shortstack{3.36e+00\\{\scriptsize$\pm$1.67e+00}}} & \adjustbox{angle=90}{\shortstack{2.97e+00\\{\scriptsize$\pm$2.45e+00}}} & \adjustbox{angle=90}{\shortstack{3.69e+00\\{\scriptsize$\pm$3.77e+00}}} & \adjustbox{angle=90}{\shortstack{1.19e+00\\{\scriptsize$\pm$1.31e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{5.72e-01}\\{\scriptsize$\pm$\textbf{2.29e-01}}}} & \adjustbox{angle=90}{\shortstack{1.70e+00\\{\scriptsize$\pm$2.52e+00}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{6.44e+00\\{\scriptsize$\pm$3.55e+00}}} & \adjustbox{angle=90}{\shortstack{2.59e+02\\{\scriptsize$\pm$2.32e+01}}} & \adjustbox{angle=90}{\shortstack{5.62e+00\\{\scriptsize$\pm$5.63e+00}}} & \adjustbox{angle=90}{\shortstack{6.15e+00\\{\scriptsize$\pm$6.22e+00}}} & \adjustbox{angle=90}{\shortstack{6.27e+00\\{\scriptsize$\pm$3.25e+00}}} & \adjustbox{angle=90}{\shortstack{7.51e+00\\{\scriptsize$\pm$6.85e+00}}} & \adjustbox{angle=90}{\shortstack{4.02e+00\\{\scriptsize$\pm$4.87e+00}}} & \adjustbox{angle=90}{\shortstack{4.54e+00\\{\scriptsize$\pm$2.92e+00}}} & \adjustbox{angle=90}{\shortstack{4.86e+00\\{\scriptsize$\pm$2.39e+00}}} & \adjustbox{angle=90}{\shortstack{5.44e+00\\{\scriptsize$\pm$4.58e+00}}} & \adjustbox{angle=90}{\shortstack{7.13e+00\\{\scriptsize$\pm$5.28e+00}}} & \adjustbox{angle=90}{\shortstack{1.57e+00\\{\scriptsize$\pm$1.41e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{6.51e-01}\\{\scriptsize$\pm$\textbf{2.62e-01}}}} & \adjustbox{angle=90}{\shortstack{2.95e+00\\{\scriptsize$\pm$2.48e+00}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:StretchedV}}} & 100 & \adjustbox{angle=90}{\shortstack{3.46e+01\\{\scriptsize$\pm$1.02e+02}}} & \adjustbox{angle=90}{\shortstack{7.47e+01\\{\scriptsize$\pm$3.00e+01}}} & \adjustbox{angle=90}{\shortstack{9.31e+01\\{\scriptsize$\pm$1.50e+02}}} & \adjustbox{angle=90}{\shortstack{6.92e+01\\{\scriptsize$\pm$1.26e+02}}} & \adjustbox{angle=90}{\shortstack{5.46e+01\\{\scriptsize$\pm$1.19e+02}}} & \adjustbox{angle=90}{\shortstack{4.60e+01\\{\scriptsize$\pm$3.09e+01}}} & \adjustbox{angle=90}{\shortstack{7.73e+01\\{\scriptsize$\pm$1.23e+02}}} & \adjustbox{angle=90}{\shortstack{4.54e+01\\{\scriptsize$\pm$9.00e+01}}} & \adjustbox{angle=90}{\shortstack{3.35e+01\\{\scriptsize$\pm$9.50e+01}}} & \adjustbox{angle=90}{\shortstack{5.10e+01\\{\scriptsize$\pm$1.05e+02}}} & \adjustbox{angle=90}{\shortstack{4.23e+01\\{\scriptsize$\pm$1.18e+02}}} & \adjustbox{angle=90}{\shortstack{9.30e+00\\{\scriptsize$\pm$5.52e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{3.39e-02}\\{\scriptsize$\pm$\textbf{1.58e-01}}}} & \adjustbox{angle=90}{\shortstack{1.61e+01\\{\scriptsize$\pm$6.29e+01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{1.36e+01\\{\scriptsize$\pm$5.74e+01}}} & \adjustbox{angle=90}{\shortstack{1.52e+03\\{\scriptsize$\pm$1.78e+02}}} & \adjustbox{angle=90}{\shortstack{9.79e+01\\{\scriptsize$\pm$1.82e+02}}} & \adjustbox{angle=90}{\shortstack{8.84e+01\\{\scriptsize$\pm$1.10e+02}}} & \adjustbox{angle=90}{\shortstack{3.54e+01\\{\scriptsize$\pm$5.75e+01}}} & \adjustbox{angle=90}{\shortstack{3.59e+02\\{\scriptsize$\pm$3.17e+02}}} & \adjustbox{angle=90}{\shortstack{2.84e+02\\{\scriptsize$\pm$2.75e+02}}} & \adjustbox{angle=90}{\shortstack{1.23e+02\\{\scriptsize$\pm$1.83e+02}}} & \adjustbox{angle=90}{\shortstack{1.87e+01\\{\scriptsize$\pm$3.21e+01}}} & \adjustbox{angle=90}{\shortstack{2.41e+02\\{\scriptsize$\pm$3.31e+02}}} & \adjustbox{angle=90}{\shortstack{6.38e+01\\{\scriptsize$\pm$9.18e+01}}} & \adjustbox{angle=90}{\shortstack{4.44e+00\\{\scriptsize$\pm$9.26e+00}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{1.53e+00}\\{\scriptsize$\pm$\textbf{1.04e+01}}}} & \adjustbox{angle=90}{\shortstack{4.34e+01\\{\scriptsize$\pm$5.45e+01}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{2.97e+01\\{\scriptsize$\pm$8.47e+01}}} & \adjustbox{angle=90}{\shortstack{3.90e+03\\{\scriptsize$\pm$2.93e+02}}} & \adjustbox{angle=90}{\shortstack{1.82e+02\\{\scriptsize$\pm$3.85e+02}}} & \adjustbox{angle=90}{\shortstack{1.43e+02\\{\scriptsize$\pm$2.40e+02}}} & \adjustbox{angle=90}{\shortstack{5.59e+01\\{\scriptsize$\pm$7.20e+01}}} & \adjustbox{angle=90}{\shortstack{7.18e+02\\{\scriptsize$\pm$6.65e+02}}} & \adjustbox{angle=90}{\shortstack{6.94e+02\\{\scriptsize$\pm$6.71e+02}}} & \adjustbox{angle=90}{\shortstack{3.79e+02\\{\scriptsize$\pm$4.24e+02}}} & \adjustbox{angle=90}{\shortstack{3.43e+01\\{\scriptsize$\pm$4.80e+01}}} & \adjustbox{angle=90}{\shortstack{2.79e+02\\{\scriptsize$\pm$3.90e+02}}} & \adjustbox{angle=90}{\shortstack{2.07e+02\\{\scriptsize$\pm$3.02e+02}}} & \adjustbox{angle=90}{\shortstack{3.66e+01\\{\scriptsize$\pm$8.76e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{2.09e-01}\\{\scriptsize$\pm$\textbf{7.40e-01}}}} & \adjustbox{angle=90}{\shortstack{1.16e+02\\{\scriptsize$\pm$1.70e+02}}} \\
\midrule
\multirow{3}{*}{\centering\shortstack{\eqref{ben:StyblinskiTang}}} & 100 & \adjustbox{angle=90}{\shortstack{-3.27e+03\\{\scriptsize$\pm$5.06e+01}}} & \adjustbox{angle=90}{\shortstack{-3.25e+03\\{\scriptsize$\pm$7.90e+01}}} & \adjustbox{angle=90}{\shortstack{-3.27e+03\\{\scriptsize$\pm$5.00e+01}}} & \adjustbox{angle=90}{\shortstack{-3.27e+03\\{\scriptsize$\pm$4.97e+01}}} & \adjustbox{angle=90}{\shortstack{-3.27e+03\\{\scriptsize$\pm$6.21e+01}}} & \adjustbox{angle=90}{\shortstack{-3.27e+03\\{\scriptsize$\pm$5.99e+01}}} & \adjustbox{angle=90}{\shortstack{-3.27e+03\\{\scriptsize$\pm$5.25e+01}}} & \adjustbox{angle=90}{\shortstack{-3.27e+03\\{\scriptsize$\pm$5.77e+01}}} & \adjustbox{angle=90}{\shortstack{-3.23e+03\\{\scriptsize$\pm$7.66e+01}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-3.28e+03}\\{\scriptsize$\pm$\textbf{4.94e+01}}}} & \adjustbox{angle=90}{\shortstack{-3.27e+03\\{\scriptsize$\pm$3.99e+01}}} & \adjustbox{angle=90}{\shortstack{-3.27e+03\\{\scriptsize$\pm$5.07e+01}}} & \adjustbox{angle=90}{\shortstack{-3.27e+03\\{\scriptsize$\pm$3.92e+01}}} & \adjustbox{angle=90}{\shortstack{-3.26e+03\\{\scriptsize$\pm$4.75e+01}}} \\
 & 500 & \adjustbox{angle=90}{\shortstack{-1.61e+04\\{\scriptsize$\pm$1.44e+02}}} & \adjustbox{angle=90}{\shortstack{-1.39e+04\\{\scriptsize$\pm$3.22e+02}}} & \adjustbox{angle=90}{\shortstack{-1.61e+04\\{\scriptsize$\pm$1.07e+02}}} & \adjustbox{angle=90}{\shortstack{-1.61e+04\\{\scriptsize$\pm$1.17e+02}}} & \adjustbox{angle=90}{\shortstack{-1.60e+04\\{\scriptsize$\pm$1.62e+02}}} & \adjustbox{angle=90}{\shortstack{-1.61e+04\\{\scriptsize$\pm$1.31e+02}}} & \adjustbox{angle=90}{\shortstack{-1.61e+04\\{\scriptsize$\pm$1.22e+02}}} & \adjustbox{angle=90}{\shortstack{-1.61e+04\\{\scriptsize$\pm$1.53e+02}}} & \adjustbox{angle=90}{\shortstack{-1.59e+04\\{\scriptsize$\pm$1.46e+02}}} & \adjustbox{angle=90}{\shortstack{-1.61e+04\\{\scriptsize$\pm$1.35e+02}}} & \adjustbox{angle=90}{\shortstack{-1.61e+04\\{\scriptsize$\pm$1.08e+02}}} & \adjustbox{angle=90}{\shortstack{-1.61e+04\\{\scriptsize$\pm$1.45e+02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-1.62e+04}\\{\scriptsize$\pm$\textbf{1.09e+02}}}} & \adjustbox{angle=90}{\shortstack{-1.62e+04\\{\scriptsize$\pm$1.16e+02}}} \\
 & 1000 & \adjustbox{angle=90}{\shortstack{-3.20e+04\\{\scriptsize$\pm$1.96e+02}}} & \adjustbox{angle=90}{\shortstack{-2.66e+04\\{\scriptsize$\pm$1.13e+03}}} & \adjustbox{angle=90}{\shortstack{-3.21e+04\\{\scriptsize$\pm$2.04e+02}}} & \adjustbox{angle=90}{\shortstack{-3.20e+04\\{\scriptsize$\pm$2.29e+02}}} & \adjustbox{angle=90}{\shortstack{-3.19e+04\\{\scriptsize$\pm$2.55e+02}}} & \adjustbox{angle=90}{\shortstack{-3.21e+04\\{\scriptsize$\pm$1.81e+02}}} & \adjustbox{angle=90}{\shortstack{-3.20e+04\\{\scriptsize$\pm$2.21e+02}}} & \adjustbox{angle=90}{\shortstack{-3.20e+04\\{\scriptsize$\pm$2.59e+02}}} & \adjustbox{angle=90}{\shortstack{-3.17e+04\\{\scriptsize$\pm$2.96e+02}}} & \adjustbox{angle=90}{\shortstack{-3.21e+04\\{\scriptsize$\pm$1.84e+02}}} & \adjustbox{angle=90}{\shortstack{-3.21e+04\\{\scriptsize$\pm$1.78e+02}}} & \adjustbox{angle=90}{\shortstack{-3.21e+04\\{\scriptsize$\pm$2.19e+02}}} & \adjustbox{angle=90}{\shortstack{-3.22e+04\\{\scriptsize$\pm$1.30e+02}}} & \adjustbox{angle=90}{\cellcolor{lightgray} \shortstack{\textbf{-3.22e+04}\\{\scriptsize$\pm$\textbf{1.57e+02}}}} \\
\midrule
\end{longtable}

The final average performance of each algorithm, evaluated on each benchmark problem and for each tested dimensionality, is summarised in Table~\ref{tab:final_results}. The table reports the mean final fitness values along with the corresponding standard deviations. For each problem and dimensionality, the best-performing algorithm is indicated in boldface and highlighted with a light grey cell background.

To assess the significance of performance differences observed among the tested algorithms a comprehensive statistical analysis was conducted. The Shapiro–Wilk test ($\alpha = 0.05$) was first applied to evaluate the normality assumption for each algorithm's results; the null hypothesis of normality was rejected for most cases in all tested variants. Consequently, the non-parametric Kruskal–Wallis test was employed, revealing statistically significant differences in the distributions of final fitness values across the algorithm configurations. To identify specific pairwise differences, Dunn’s post-hoc test with Benjamini-Hochberg correction \citep{haynes2013benjaminihochberg} was used to control the false discovery rate in multiple comparisons. This procedure identified 92 algorithm pairs for which the differences were not statistically significant ($p > 0.05$): 29 pairs for the 100-dimensional case, 33 pairs for 500 dimensions, and 30 pairs for 1000 dimensions.
%
Table~\ref{tab:dunnfail} lists 12 selected pairs involving the baseline algorithms (PSO and PerturbationPSO) that were not found to differ significantly from at least one of the best-performing configurations.


\begin{longtable}{llp{0.5\textwidth}r}
\caption[Non-significant pairwise differences from Dunn's test]{Non-significant pairwise differences involving baseline algorithms and best-performing algorithms based on Dunn’s test with Benjamini–Hochberg adjustment ($p > 0.05$).}
\label{tab:dunnfail}
\\
\toprule
\textbf{Problem} & \textbf{$d$} & \textbf{Pair} & \textbf{p-value} \\
\midrule
\multirow{3}{*}{Mishra N3}
    & 100  & HybridAdditivePSO vs PerturbationPSO        & 0.7533 \\
    & 500  & HybridAdditivePSO vs PerturbationPSO        & 0.4285 \\
    & 1000 & HybridAdditivePSO vs PerturbationPSO        & 0.3458 \\
\midrule
\multirow{1}{*}{Mishra N4}
    & 500  & HybridAdditivePSO vs PerturbationPSO        & 0.3022 \\
\midrule
\multirow{3}{*}{Shifted Schwefel}
    & 100  & HybridFullDisjointPSO vs PerturbationPSO    & 0.9049 \\
    & 500  & HybridFullDisjointPSO vs PerturbationPSO    & 0.8832 \\
    & 1000 & HybridFullDisjointPSO vs PerturbationPSO    & 0.2817 \\
\midrule
\multirow{3}{*}{Shubert N4}
    & 100  & HybridPartialDisjointPSO vs PerturbationPSO & 0.6407 \\
    & 500  & HybridPartialDisjointPSO vs PerturbationPSO & 0.8980 \\
    & 1000 & HybridPartialDisjointPSO vs PerturbationPSO & 0.9992 \\
\midrule
\multirow{2}{*}{Generalized Schaffer N1}
    & 500  & ContrarianPSO vs PSO                        & 0.4325 \\
    & 1000 & ContrarianPSO vs PSO                        & 0.2941 \\
\bottomrule
\end{longtable}










\section{Discussion}

Across virtually all benchmark problems and tested dimensionalities, the proposed hybrid PSO variants---particularly HybridPartialDisjointPSO and HybridAdditivePSO---consistently achieve significantly better final fitness values than the standard PSO. This superiority is evident in both the convergence curves and the distribution plots on Figures~\ref{fig:results100}–\ref{fig:results1000}, and is quantitatively confirmed by their leading counts of best-performing placements reported in Table~\ref{tab:algo-top1-counts}.

\begin{longtable}[c]{p{5cm}cccc}
\caption[Frequency of best results by algorithm and dimension]{Number of times each algorithm achieved the best (top-1) result for each tested dimensionality and overall.}
\label{tab:algo-top1-counts} \\
\toprule
\multirow{2}{*}{\textbf{Algorithm}} & \multicolumn{3}{c}{$d$} & \multirow{2}{*}{\textbf{Total}}  \\
\cmidrule(lr){2-4}
 & \textbf{100} & \textbf{500} & \textbf{1000} \\ \midrule
\endfirsthead

\multicolumn{5}{c}%
{{\textit{\bfseries Table \thetable\ continued from previous page.}}} \\
\toprule
\multirow{2}{*}{\textbf{Algorithm}} & \multicolumn{3}{c}{$d$} & \multirow{2}{*}{\textbf{Total}}  \\
\cmidrule(lr){2-4}
 & \textbf{100} & \textbf{500} & \textbf{1000} \\ \midrule
\endhead

\bottomrule
\addlinespace[1mm]
\multicolumn{5}{r}%
{{\textit{Continued on the next page.}}} \\
\endfoot

\bottomrule
\endlastfoot

HybridPartialDisjointPSO & 14 & 18 & 17 & \textbf{49} \\
PerturbationPSO         & 6  & 6  & 5  & \textbf{17} \\
RebelPSO                & 2  & 2  & 2  & \textbf{6}  \\
HybridAdditivePSO       & 2  & 0  & 3  & \textbf{5}  \\
ContrarianPSO           & 1  & 2  & 2  & \textbf{5}  \\
ContrarianDefeatistPSO  & 1  & 2  & 1  & \textbf{4}  \\
RebelRejectorPSO        & 2  & 1  & 1  & \textbf{4}  \\
HybridFullDisjointPSO   & 1  & 1  & 1  & \textbf{3}  \\
DefeatistPSO            & 2  & 0  & 0  & \textbf{2}  \\
EscapistPSO             & 1  & 0  & 0  & \textbf{1}  \\
\end{longtable}

On challenging, ill-conditioned problems such as Rotated Bent Cigar and Rotated Discus, the final average best fitness achieved by HybridPartialDisjointPSO is often orders of magnitude lower than that of standard PSO, demonstrating vastly improved accuracy. On highly multimodal landscapes, including Egg-Holder and Schwefel~N6, the hybrid variants similarly outperform PSO by substantial margins, indicating effective global search capability and strong resilience to deceptive local minima. Even on relatively smoother problems (e.g., Alpine N1, Salomon), the hybrids converge to superior optima while maintaining markedly tighter fitness distributions, suggesting greater repeatability and reliability. The consistently strong results and narrow final fitness spread (as evident in the violin plots for Alpine N1, Egg-Holder, and Stretched~V) further highlight their dependable search performance.
While HybridAdditivePSO occasionally exhibits slightly higher variance than its partial disjoint counterpart---reflected in wider violin plots on certain problems such as Stretched V at 500 dimensions---its median performance remains excellent, showcasing its potent and adaptive exploratory capacity. Notably, the Dunn’s test results frequently indicate that these two hybrid strategies are statistically indistinguishable when both are among the top performers, underscoring their comparable effectiveness at the highest performance level.
A few isolated exceptions emerge on specific landscapes (e.g., Crowned Cross, Expanded Shaffer), where targeted single-role variants such as RebelRejectorPSO or ContrarianPSO outperform both hybrids and the standard PSO. This behavior points to landscape-specific synergies and supports the potential benefit of incorporating adaptive role selection mechanisms in future algorithm designs.





\begin{longtable}[c]{p{5cm}cccc}
\caption[Frequency of worst results by algorithm and dimension]{Number of times each algorithm achieved the worst performance (Top-1 worst) for each tested dimensionality and overall.}
\label{tab:algo-worst1-counts} \\
\toprule
\multirow{2}{*}{\textbf{Algorithm}} & \multicolumn{3}{c}{$d$} & \multirow{2}{*}{\textbf{Total}}  \\
\cmidrule(lr){2-4}
 & \textbf{100} & \textbf{500} & \textbf{1000} \\ \midrule
\endfirsthead

\multicolumn{5}{c}%
{{\textit{\bfseries Table \thetable\ continued from previous page.}}} \\
\toprule
\multirow{2}{*}{\textbf{Algorithm}} & \multicolumn{3}{c}{$d$} & \multirow{2}{*}{\textbf{Total}}  \\
\cmidrule(lr){2-4}
 & \textbf{100} & \textbf{500} & \textbf{1000} \\ \midrule
\endhead

\bottomrule
\addlinespace[1mm]
\multicolumn{5}{r}%
{{\textit{Continued on the next page.}}} \\
\endfoot

\bottomrule
\endlastfoot

PerturbationPSO         & 13 & 16 & 16 & \textbf{45} \\
HybridAdditivePSO       & 5  & 6  & 4  & \textbf{15} \\
HybridPartialDisjointPSO& 5  & 4  & 5  & \textbf{14} \\
ContrarianPSO           & 3  & 1  & 3  & \textbf{7}  \\
RebelPSO                & 2  & 2  & 2  & \textbf{6}  \\
PSO                     & 1  & 1  & 1  & \textbf{3}  \\
EscapistPSO             & 1  & 0  & 1  & \textbf{2}  \\
RejectorPSO             & 0  & 2  & 0  & \textbf{2}  \\
DefeatistPSO            & 1  & 0  & 0  & \textbf{1}  \\
EschewerPSO             & 1  & 0  & 0  & \textbf{1}  \\
\end{longtable}

The convergence curves further demonstrate that the hybrid methods generally do not sacrifice convergence speed for improved final accuracy. Instead, they tend to achieve steeper early-stage fitness improvements and sustain meaningful progress deeper into the optimization run. In contrast, the canonical PSO typically converges rapidly in the initial stages but plateaus prematurely, illustrating its well-known tendency to stagnate in local optima. For instance, on problems such as Modified Rosenbrock, Rotated Elliptic, and Stretched~V, HybridPartialDisjointPSO consistently achieves both faster initial convergence and superior asymptotic fitness compared to standard PSO. HybridAdditivePSO may display slightly greater early-stage variability due to its flexible role activation, but it ultimately matches or surpasses the performance of HybridPartialDisjointPSO in terms of final solution quality.

 
PerturbationPSO, designed as a simple exploration booster, generally exhibits poor convergence and high residual error. It emerges as the most frequent worst-performing algorithm, as shown in Table~\ref{tab:algo-worst1-counts}, reinforcing the conclusion that random perturbations alone are an ineffective substitute for structured, informed diversity mechanisms. It is worth noting, however, that PerturbationPSO ranks second in Top-1 counts (17 total). This apparent success is largely due to occasional wins on shifted or rotated CEC benchmark functions, where random perturbations can incidentally enhance exploration. Outside these specific cases, PerturbationPSO remains highly inconsistent and unreliable.


On the other hand, both HybridAdditivePSO and HybridPartialDisjointPSO appear in the worst-placement counts 15 and 14 times, respectively. This apparent contradiction shows that they may be often outperformed by an algorithm that is highly specialized for a given landscape. It does not necessarily imply poor absolute performance.
While counts of best and worst placements provide useful frequency information, the average rank presented on Table~\ref{tab:algo-avg-rank} offers a more stable indicator of overall competitiveness across the full test suite. A lower rank denotes consistently high performance. HybridPartialDisjointPSO again emerges as the most robust, with the lowest overall average rank (9.35), remaining consistently strong across all dimensions.
DefeatistPSO and ContrarianDefeatistPSO also exhibit excellent average ranks (9.63 and 9.67, respectively), performing comparably to or better than HybridFullDisjointPSO (10.19). This demonstrates the consistent effectiveness of strategies leveraging attraction to inferior solutions as a controlled means to escape local minima.
HybridAdditivePSO maintains a solid average rank (12.96), though slightly higher than its partial disjoint counterpart, reflecting its occasionally higher outcome variance, as seen in some of the distribution plots. Standard PSO and PerturbationPSO show distinctly weaker competitiveness, with average ranks of, respectively, 16.01 and 17.61, proving relative weakness against the more sophisticated role-based and hybrid designs.


\begin{longtable}[c]{p{5cm}cccc}
\caption[Average ranking of each algorithm across dimensions]{Average ranking of each algorithm for each dimensionality and overall (lower is better).}
\label{tab:algo-avg-rank} \\
\toprule
\multirow{2}{*}{\textbf{Algorithm}} & \multicolumn{3}{c}{$d$} & \multirow{2}{*}{\textbf{Total}}  \\
\cmidrule(lr){2-4}
 & \textbf{100} & \textbf{500} & \textbf{1000} \\ \midrule
\endfirsthead

\multicolumn{5}{c}%
{{\textit{\bfseries Table \thetable\ continued from previous page.}}} \\
\toprule
\multirow{2}{*}{\textbf{Algorithm}} & \multicolumn{3}{c}{$d$} & \multirow{2}{*}{\textbf{Total}}  \\
\cmidrule(lr){2-4}
 & \textbf{100} & \textbf{500} & \textbf{1000} \\ \midrule
\endhead

\bottomrule
\addlinespace[1mm]
\multicolumn{5}{r}%
{{\textit{Continued on the next page.}}} \\
\endfoot

\bottomrule
\endlastfoot

HybridPartialDisjointPSO & 9.90 & 9.14 & 9.02 & \textbf{9.35} \\
DefeatistPSO            & 10.05 & 9.78 & 9.08 & \textbf{9.63} \\
ContrarianDefeatistPSO  & 9.75 & 9.95 & 9.30 & \textbf{9.67} \\
HybridFullDisjointPSO   & 10.95 & 10.06 & 9.56 & \textbf{10.19} \\
HybridAdditivePSO       & 13.13 & 13.71 & 12.05 & \textbf{12.96} \\
RebelPSO                & 13.63 & 14.03 & 14.62 & \textbf{14.10} \\
RebelRejectorPSO        & 14.43 & 14.30 & 15.67 & \textbf{14.80} \\
EschewerEscapistPSO     & 14.87 & 14.44 & 15.59 & \textbf{14.97} \\
EschewerPSO             & 15.03 & 15.16 & 15.67 & \textbf{15.29} \\
EscapistPSO             & 16.57 & 15.97 & 15.10 & \textbf{15.88} \\
PSO                     & 17.06 & 16.05 & 14.90 & \textbf{16.01} \\
RejectorPSO             & 15.19 & 16.52 & 16.89 & \textbf{16.20} \\
PerturbationPSO         & 16.59 & 17.98 & 18.25 & \textbf{17.61} \\
ContrarianPSO           & 17.46 & 17.52 & 19.00 & \textbf{17.99} \\
\end{longtable}

Table~\ref{tab:algo-avg-norm} provides an additional layer of insight by presenting a min–max normalized performance score for each algorithm, which scales performance on each benchmark problem to the interval [0,1]. In this scheme, the best-performing algorithm for a given problem and dimensionality is assigned a score of 0, while the worst-performing algorithm is assigned a score of 1, and all others are scaled linearly between these extremes. This approach captures not only the ranking but also the magnitude of performance differences, offering a more nuanced comparison. Lower normalized values thus indicate better relative performance within the tested set.


\begin{longtable}[c]{p{5cm}cccc}
\caption[Average min–max normalized score by algorithm and dimension]{Average min-max normalized performance score for each algorithm (lower is better), by dimension and overall.}
\label{tab:algo-avg-norm} \\
\toprule
\multirow{2}{*}{\textbf{Algorithm}} & \multicolumn{3}{c}{$d$} & \multirow{2}{*}{\textbf{Total}}  \\
\cmidrule(lr){2-4}
 & \textbf{100} & \textbf{500} & \textbf{1000} \\ \midrule
\endfirsthead

\multicolumn{5}{c}%
{{\textit{\bfseries Table \thetable\ continued from previous page.}}} \\
\toprule
\multirow{2}{*}{\textbf{Algorithm}} & \multicolumn{3}{c}{$d$} & \multirow{2}{*}{\textbf{Total}}  \\
\cmidrule(lr){2-4}
 & \textbf{100} & \textbf{500} & \textbf{1000} \\ \midrule
\endhead

\bottomrule
\addlinespace[1mm]
\multicolumn{5}{r}%
{{\textit{Continued on the next page.}}} \\
\endfoot

\bottomrule
\endlastfoot

ContrarianDefeatistPSO   & 0.269 & 0.244 & 0.251 & \textbf{0.255} \\
DefeatistPSO             & 0.303 & 0.303 & 0.301 & \textbf{0.302} \\
HybridFullDisjointPSO    & 0.351 & 0.350 & 0.341 & \textbf{0.347} \\
HybridPartialDisjointPSO & 0.356 & 0.366 & 0.364 & \textbf{0.362} \\
RebelPSO                 & 0.356 & 0.356 & 0.380 & \textbf{0.364} \\
RebelRejectorPSO         & 0.358 & 0.378 & 0.382 & \textbf{0.373} \\
EschewerEscapistPSO      & 0.378 & 0.370 & 0.390 & \textbf{0.379} \\
ContrarianPSO            & 0.397 & 0.377 & 0.388 & \textbf{0.387} \\
HybridAdditivePSO        & 0.403 & 0.395 & 0.367 & \textbf{0.388} \\
EschewerPSO              & 0.385 & 0.387 & 0.402 & \textbf{0.391} \\
PSO                      & 0.399 & 0.394 & 0.387 & \textbf{0.393} \\
RejectorPSO              & 0.388 & 0.406 & 0.406 & \textbf{0.400} \\
EscapistPSO              & 0.406 & 0.417 & 0.418 & \textbf{0.414} \\
PerturbationPSO          & 0.608 & 0.663 & 0.683 & \textbf{0.651} \\
\end{longtable}

Here, ContrarianDefeatistPSO (0.255) and DefeatistPSO (0.302) achieve the best scores overall, highlighting the remarkable consistency of negative-learning roles when considering not only placement but also the ``degree of optimality.'' The leading hybrid variants follow closely, with HybridFullDisjointPSO, HybridPartialDisjointPSO, and HybridAdditivePSO scoring 0.347, 0.362, and 0.388, respectively. Standard PSO (0.393) and PerturbationPSO (0.651) confirm their mid-tier or poor relative performance.

A few clear patterns emerge from the combined quantitative and visual analyses. First,
both above-mentioned hybrid strategies consistently outperform the standard PSO and simpler role-based variants across a wide spectrum of problem types, including separable, non-separable, rotated, shifted, unimodal, and highly multimodal functions. Nonetheless, single-role variants can occasionally match or even surpass the hybrids on problems with particular structural features; for example, ContrarianPSO performs exceptionally well on the Expanded Shaffer function, where deliberate attraction to poorer regions helps escape deceptive local basins. As dimensionality increases (from 100 to 1000 variables), the performance gap between the standard PSO and the hybrid approaches widens, confirming the hybrids’ scalability and greater resilience to the ``curse of dimensionality.'' While PerturbationPSO occasionally achieves competitive results, it exhibits high variance in both average performance and final outcomes, which indicates lower reliability compared to more structured diversity mechanisms.



































}